---
title: 'Tanzania Market Survey C: Descriptive Analysis'
author: "Beth Savagar"
date: "2024-01-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)

```

```{r libraries, include = F}
library(readr)
library(tidyverse)
library(sf)
library(ggplot2)
library(here)
library(knitr)
library(ggpubr)
library(RColorBrewer)
library(rmarkdown)

```

```{r theme, include = F}
custom_theme <- theme_bw() + 
  theme(text = element_text(family = "serif", size = 10))
theme_set(custom_theme)

tanzania_pal <- rep(brewer.pal(9,"Pastel1"),times=4)
market_pal <- c(brewer.pal(8, "Dark2"), "#FFA500", "#6A3D9A", "#33A02C")
```

```{r load-data, include = F}

# Market survey A data:
mrkta_gps <- read_csv(here("data/tanzania_data/mrkta_gps_tanzania_final.csv")) %>%
  select(-`...1`)
mrkta_info <-  read_csv(here("data/tanzania_data/mrkta_generalinfo_tanzania_final.csv")) %>%
  select(-`...1`)
mrkta_spatial <- read_csv(here("data/tanzania_data/mrkta_withfeatures_tanzania_final.csv"))

# Market Survey B data
mrktb_info <- read_csv(here("data/tanzania_data/mrktb_generalinfo_tanzania_final.csv")) %>%
  select(-`...1`)

# Market Survey C data
mrktc_gps <- read_csv(here("data/tanzania_data/mrktc_allgps_tanzania_final.csv")) %>%
  select(-`...1`)
mrktc_info <-  read_csv(here("data/tanzania_data/mrktc_generalinfo_tanzania_final.csv")) %>%
  select(-`...1`)
mrktc_actvty <- read_csv(here("data/data-cleaning_data/mrktc_mrktactivities_tanzania_final.csv"))
# write.csv(mrktc_actvty, file = "data/data-cleaning_data/mrktc_mrktactivities_tanzania_final.csv")

```

# Data Overview:

Market Identifiers:
- fid
- date
- region
- district
- district20
- ward
- village
- market

## 1) Market Characteristics: 

### (i) Environment

- humpop_density1km
- shppop_10km
- gtpop_10km
- anmlpop_10km
- prod.sys
- town.distkm
- town.type
- road.distkm
- road.type

Data Sources:
- WorldPop Data (via HumData Exchange)
- GLW Data (FAO)
- Africover (FAO - via HumData Exchange)

```{r spatial}

mrkts_master_v1 <- mrkta_spatial

```

### (ii) Size & structure

- num.srvy (C)
- num.sales (A)
- num.anmls (B) 
- prop.shp (B)
- prop.goat (B)
- prop.shpA (B)
- prop.shpY (B)
- prop.goatA (B)
- prop.goatY (B)


```{r mrkta, include = F}

head(mrkta_info)

num.srvy <- mrktc_gps %>% 
  group_by(region,district20,ward,village,market) %>%
  summarise(num.srvy = n())

num.sales <- mrkta_info %>%
  mutate(`3c.all.sales` = `3a.sheep.sales` + `3b.goat.sales`) %>%
  select(fid, 
         num.sales = `3c.all.sales`,
         shp.sales = `3a.sheep.sales`,
         goat.sales = `3b.goat.sales`)

num.anmlsdf <- mrktb_info %>%
  select(fid,
         region,
         district,
         district20,
         ward,
         village,
         market,
         market.type, 
         starts_with("sheep."), 
         starts_with("goat."), 
         -"date.final") %>%
  rowwise() %>% 
  mutate(num.anmls = sum(c_across(`sheep.0to12`:`goat.adult`), na.rm = T)) %>%
  ungroup() %>%
  mutate(
    prop.shp = (sheep.0to12+sheep.adult)/num.anmls,
    prop.goat = (goat.0to12+goat.adult)/num.anmls,
    prop.shpY = sheep.0to12/num.anmls,
    prop.shpA = sheep.adult/num.anmls,
    prop.goatY = goat.0to12/num.anmls,
    prop.goatA = goat.adult/num.anmls) %>%
  select(
         region,
         district,
         district20,
         ward,
         village,
         market, 
         num.anmls, 
         starts_with("prop."))

num.anmlsdf <- num.anmlsdf %>%
  # calc most animals sold:
  rowwise() %>%
  mutate(main.anml = names(num.anmlsdf %>% select(prop.shpY:prop.goatA))[which.max(c_across(c(prop.shpY:prop.goatA)))],
         main.anml = gsub("prop.", "", main.anml)) %>%
  ungroup()

mrkts_master_v2 <- mrkts_master_v1 %>%
  left_join(num.srvy,
            by = c("region",
                   "district20",
                   "ward",
                   "village",
                   "market")) %>%
  left_join(num.sales, 
            by = "fid") %>%
  left_join(num.anmlsdf, 
            by = c("region",
                   "district",
                   "district20",
                   "ward",
                   "village",
                   "market"))

  
```

## 2) Market Catchment Characteristics:

* Not yet available *

```{r mrktcathement}

# mrkts_master_v3 <- mrkts_master_v2

```


## 3) Stakeholder Characteristics:

(i) Stakeholder activities at market:

- activity.main
- prop.trader
- prop.buy
-	prop.sell
-	prop.trade
-	prop.middleman
-	prop.otheractvty
	
(ii) Stakeholder market attendance	

- visits.othermrkt
-	visits.thismrkt

(iii) Trade (buy,sell) reason


```{r mrktc, include = F}

head(mrktc_info)

mrktc_characteristics <- mrktc_info %>%
  left_join(mrktc_actvty, by = "fid") %>%
  group_by(region,district20,ward,village,market) %>%
  summarise(
    num.srvy = n(),
    
    # 3) Stakeholder Characteristics 
    
    # (i) Stakeholder activity 
    # actvty.main = ###
    prop.trader = sum(trader)/num.srvy,

    # prop of stakeholders undertaking X activity:
    prop.buy = sum(`1.activity.buy`)/num.srvy,
    prop.sell = sum(`1.activity.sell`)/num.srvy,
    prop.middleman = sum(`1.activity.middleman`)/num.srvy,
    prop.trade = sum(`1.activity.trade`)/num.srvy, 
    prop.slaughter = sum(`1.activity.slaughter`)/num.srvy, 
    prop.food = sum(`1.activity.food`)/num.srvy, 
    prop.otheractvty = sum(`1.activity.other`)/num.srvy,
    prop.multiactvty = sum(`1.activity.multi`)/num.srvy,
    
    # num.buy = sum(`1.activity.buy`), # for calcs
    # num.sell = sum(`1.activity.sell`), # for calcs
    
    # (ii) Stakeholder market attendance
    visits.thismrkt = sum(na.omit(`12.buy.sell.per.month`))/num.srvy,
    visits.othermrkt = mean(`number.markets.visited`),
    
    # (iii) Stakeholder motivation (TBC)
    ## Sales
    sellreason.business = sum(`3.sell.business`)/num.srvy,
    sellreason.household = sum(`3.sell.household`)/num.srvy,
    sellreason.medical = sum(`3.sell.medical`)/num.srvy,
    sellreason.school = sum(`3.sell.school`)/num.srvy,
    sellreason.livestocktreatment = sum(`3.sell.livestocktreatment`)/num.srvy,
    sellreason.restock = sum(`3.sell.restock`)/num.srvy,
    sellreason.religious = sum(`3.sell.religious`)/num.srvy,
    sellreason.slaughter = sum(`3.sell.slaughter`)/num.srvy,
    sellreason.income = sum(`3.sell.income`)/num.srvy,
    sellreason.agriculture = sum(`3.sell.agriculture`)/num.srvy,
    sellreason.food = sum(`3.sell.food`)/num.srvy,
    sellreason.otherreason = sum(`3.sell.otherreason`)/num.srvy,
    sellreason.multi = sum(`3.sellreason.multi`)/num.srvy,
    
    ## Purchases:
    buyreason.business = sum(`7.buy.business`)/num.srvy,
    buyreason.restock = sum(`7.buy.restock`)/num.srvy,
    buyreason.breedstock = sum(`7.buy.breedstock`)/num.srvy,
    buyreason.fattening = sum(`7.buy.fattening`)/num.srvy,
    buyreason.rearing = sum(`7.buy.rearing`)/num.srvy,
    buyreason.homeconsumption = sum(`7.buy.homeconsumption`)/num.srvy,
    buyreason.religious = sum(`7.buy.religious`)/num.srvy,
    buyreason.slaughter = sum(`7.buy.slaughter`)/num.srvy,
    buyreason.income = sum(`7.buy.income`)/num.srvy,
    buyreason.informaltrade = sum(`7.buy.informaltrade`)/num.srvy,
    buyreason.food = sum(`7.buy.food`)/num.srvy,
    buyreason.otherreason = sum(`7.buy.otherreason`)/num.srvy,
    buyreason.multi = sum(`7.buyreason.multi`)/num.srvy,
    
    # 4) Origin Characteristics 

    # (i) origin placetype (/num.sell)
    origin.village = sum(`2.sell.village`)/num.srvy,
    origin.town = sum(`2.sell.town`)/num.srvy,
    origin.market = sum(`2.sell.market`)/num.srvy,
    origin.abattoir = sum(`2.sell.abattoir`)/num.srvy,
    origin.otherplace = sum(`2.sell.otherplace`)/num.srvy,

    # (ii) origin transport type: (/num.sell)
    origin.foot = sum(`4.sell.foot`)/num.srvy,
    origin.vehicle = sum(`4.sell.vehicle`)/num.srvy,
    origin.cart = sum(`4.sell.cart`)/num.srvy,
    origin.frommrkt = sum(`4.sell.frommrkt`)/num.srvy,
    origin.othertransport = sum(`4.sell.othertransport`)/num.srvy,
    origin.unknowntransport = sum(`4.sell.unknowntransport`)/num.srvy,

    # 5) Destination Characteristics 

    # (i) destination placetype (/num.buy?)
    dest.village = sum(`6.buy.village`)/num.srvy,
    dest.town = sum(`6.buy.town`)/num.srvy,
    dest.market = sum(`6.buy.market`)/num.srvy,
    dest.abattoir = sum(`6.buy.abattoir`)/num.srvy,
    dest.otherplace = sum(`6.buy.otherplace`)/num.srvy,

    # (ii) destination transport type: (/num.buy?)
    dest.foot = sum(`8.buy.foot`)/num.srvy,
    dest.vehicle = sum(`8.buy.vehicle`)/num.srvy,
    dest.cart = sum(`8.buy.cart`)/num.srvy,
    dest.motorbike = sum(`8.buy.motorbike`)/num.srvy,
    dest.mrktslaughter = sum(`8.buy.slaughter`)/num.srvy,
    dest.atmrkt = sum(`8.buy.atmarket`)/num.srvy,
    dest.othertransport = sum(`8.buy.othertransport`)/num.srvy,
    dest.unknowntransport = sum(`8.buy.unknowntransport`)/num.srvy,

  ) %>%
  ungroup()



mrktc_forjoin <- mrktc_characteristics %>%
  rowwise() %>%
  mutate(
    # main activity
    actvty.main = names(mrktc_characteristics %>% select(prop.buy:prop.otheractvty))[which.max(c_across(c(prop.buy:prop.otheractvty)))],
    
    # main sell reason
    sellreason.main = names(mrktc_characteristics %>% select(sellreason.business:sellreason.otherreason))[which.max(c_across(c(sellreason.business:sellreason.otherreason)))],
    
    # main buy reason
    buyreason.main = names(mrktc_characteristics %>% select(buyreason.business:buyreason.otherreason))[which.max(c_across(c(buyreason.business:buyreason.otherreason)))],
    
    # main origin type
    origin.main = names(
      mrktc_characteristics %>% select(origin.village:origin.otherplace)
    )[which.max(c_across(c(origin.village:origin.otherplace)))],
    # main origin transport
    origin.transport.main = names(
      mrktc_characteristics %>% select(origin.foot:origin.unknowntransport)
    )[which.max(c_across(c(origin.foot:origin.unknowntransport)))],
    # main destination
    dest.main = names(
      mrktc_characteristics %>% select(dest.village:dest.otherplace)
    )[which.max(c_across(c(dest.village:dest.otherplace)))],
    # main destination transport
    dest.transport.main = names(
      mrktc_characteristics %>% select(dest.foot:dest.unknowntransport)
    )[which.max(c_across(c(dest.foot:dest.unknowntransport)))]
  ) %>%
  ungroup() %>%
  select(
    region,
    district20,
    ward,
    village,
    market,
    
    #stakeholder characteristics
    prop.trader,
    actvty.main,
    prop.buy,
    prop.sell,
    prop.trade,
    prop.middleman,
    prop.otheractvty,
    
    visits.othermrkt,
    visits.thismrkt,
    
    # stakeholder motivation (sales)
    sellreason.main,
    sellreason.business,
    sellreason.household,
    sellreason.medical,
    sellreason.school,
    sellreason.livestocktreatment,
    sellreason.restock,
    sellreason.religious,
    sellreason.slaughter,
    sellreason.income,
    sellreason.agriculture,
    sellreason.food,
    sellreason.otherreason,
    
    # stakehold motivation (purchases)
    buyreason.main,
    buyreason.business,
    buyreason.restock,
    buyreason.breedstock,
    buyreason.fattening,
    buyreason.rearing,
    buyreason.homeconsumption,
    buyreason.religious,
    buyreason.slaughter,
    buyreason.income,
    buyreason.informaltrade,
    buyreason.food,
    buyreason.otherreason,
    
    # origin characteristics
    origin.main,
    origin.village,
    origin.town,
    origin.market,
    origin.abattoir,
    origin.otherplace,
    
    origin.transport.main,
    origin.foot,
    origin.vehicle,
    origin.cart,
    origin.othertransport,
    origin.unknowntransport,
    
    # destination characteristics
    dest.main,
    dest.village,
    dest.town,
    dest.market,
    dest.abattoir,
    dest.otherplace,
    
    dest.transport.main,
    dest.foot,
    dest.vehicle,
    dest.cart,
    dest.othertransport,
    dest.unknowntransport,
  ) %>%
  ungroup()



mrkts_master_v4 <- mrkts_master_v3 %>%
  left_join(mrktc_forjoin,
            by = c("region", "district20","ward","village","market"))

```


## 4) Market Survey C, Part II (Activities):

- For purpose of market type definition and MVA, Market Survey C, part II provides:
    - Activity at market for each respondent 
      - *Summarised as proportion respondents undertaking X activity at market*
    - Number of times each respondent visits the market (to buy/sell) each month:
      - *Summarised as mean visits to the market per month*
    - Origin placetypes for animals sold at the market
      - *Summarised as proportion of origin placetypes for animals sold at market*
    - Origin transport for animals sold at the market
      - *Summarised as proportion of origin transport types for animals sold at market*
    - Destination placetypes for animals bought at the market
      - *Summarised as proportion animals destination placetypes for animals bought at market*
    - Destination transport for animals sold at the market
      - *Summarised as proportion of destination transport types for animals bought at market*

```{r mrktcactivities, include = F}

# prop.buy	prop.sell	prop.trade	prop.broker	prop.otheractvty	prop.multiactvty	main.actvty
# origin.placetype	origin.village	origin.town	origin.market	origin.abattoir

colnames(mrktc_actvty)

mrktc_actvty_summary <- mrktc_info %>%
  select(fid, ends_with(".final")) %>% 
  left_join(mrktc_actvty, by = "fid") %>%
  group_by(region.final, district.final, ward.final, village.final, market.final) %>%
  summarise(
    num.srvy = n(),
    
    # market activity
    prop.buy = sum(`1.activity.buy`)/num.srvy,
    prop.sell = sum(`1.activity.sell`)/num.srvy,
    prop.middleman = sum(`1.activity.middleman`)/num.srvy,
    prop.trade = sum(`1.activity.trade`)/num.srvy, 
    prop.otheractvty = sum(`1.activity.other`)/num.srvy,
    prop.multiactvty = sum(`1.activity.multi`)/num.srvy,
    # actvty.main = ###
    
    # origin placetype
    origin.village = sum(`2.sell.village`)/num.srvy,
    origin.town = sum(`2.sell.town`)/num.srvy,
    origin.market = sum(`2.sell.market`)/num.srvy,
    origin.abattoir = sum(`2.sell.abattoir`)/num.srvy,
    origin.otherplace = sum(`2.sell.otherplace`)/num.srvy,
    # origin.main = ###
    
    # origin transport type:
    origin.foot = sum(`4.sell.foot`)/num.srvy,
    origin.vehicle = sum(`4.sell.vehicle`)/num.srvy,
    origin.cart = sum(`4.sell.cart`)/num.srvy,
    origin.othertransport = sum(`4.sell.othertransport`)/num.srvy,
    origin.unknowntransport = sum(`4.sell.unknowntransport`)/num.srvy,
    # origin.transport.main = ###
    
    # destination placetype
    dest.village = sum(`6.buy.village`)/num.srvy,
    dest.town = sum(`6.buy.town`)/num.srvy,
    dest.market = sum(`6.buy.market`)/num.srvy,
    dest.abattoir = sum(`6.buy.abattoir`)/num.srvy,
    dest.otherplace = sum(`6.buy.otherplace`)/num.srvy,
    # dest.main = ###
    
    # destination transport type:
    dest.foot = sum(`8.buy.foot`)/num.srvy,
    dest.vehicle = sum(`8.buy.vehicle`)/num.srvy,
    dest.cart = sum(`8.buy.cart`)/num.srvy,
    dest.othertransport = sum(`8.buy.othertransport`)/num.srvy,
    dest.unknowntransport = sum(`8.buy.unknowntransport`)/num.srvy,
    # dest.transport.main = ###
    
    # mean buy/sell at market each month (ignore NA)
    buysell.month = sum(na.omit(`12.buy.sell.per.month`))/num.srvy)  %>%
  ungroup() %>% 
  select(ends_with(".final"), 
         starts_with("num."),
         starts_with("prop."),
         starts_with("origin."),
         starts_with("dest"),
         "buysell.month")


mrktc_actvty_forjoin <- mrktc_actvty_summary %>%
  rowwise() %>%
  mutate(
    prop.actvty.main = names(mrktc_actvty_summary %>% select(prop.buy:prop.otheractvty))[which.max(c_across(c(prop.buy:prop.otheractvty)))],
    origin.main = names(mrktc_actvty_summary %>% select(origin.village:origin.otherplace))[which.max(c_across(c(origin.village:origin.otherplace)))],
    origin.transport.main = names(mrktc_actvty_summary %>% select(origin.foot:origin.unknowntransport))[which.max(c_across(c(origin.foot:origin.unknowntransport)))],
    dest.main = names(mrktc_actvty_summary %>% select(dest.village:dest.otherplace))[which.max(c_across(c(dest.village:dest.otherplace)))],
    dest.transport.main = names(mrktc_actvty_summary %>% select(dest.foot:dest.unknowntransport))[which.max(c_across(c(dest.foot:dest.unknowntransport)))]
    ) %>%
   ungroup() %>% 
  select(ends_with(".final"), 
         starts_with("town."),
         starts_with("num."),
         starts_with("prop."),
         starts_with("origin."),
         starts_with("dest"),
         "buysell.month")
  
  
mrkts_master_v4 <- mrkts_master_v3 %>%
  left_join(mrktc_actvty_forjoin %>% select(-num.srvy),
            by = c("region.final", "district.final","ward.final","village.final","market.final"))


```


# Market Characteristics:

Market surveys were filtered to **exclude** markets in Mtwara region

Markets in Ruvuma and Lindi (1 market each) were also excluded 
  - Visited as part of Mtwara surveys

```{r mrktsmasterNomtwara, include = F}
mrkts_master_noMtwara <- mrkts_master_v4 %>% filter(!region.final %in% c("mtwara", "lindi", "ruvuma"))

```

## (1) Number of surveys per market:

- *NA's correspond to markets in survey A which are not found in survey C*

```{r mrktsrvy}

num_srvy <- nrow(mrkts_master_noMtwara)
print(paste(num_srvy, "markets were surveyed, excluding Mtwara markets"))

mrkts_master_noMtwara %>%
  summarise(
    min = min(num.srvy, na.rm = TRUE), 
    q1 = quantile(num.srvy, 0.25, na.rm = TRUE), 
    median = median(num.srvy, na.rm = TRUE), 
    mean = mean(num.srvy, na.rm = TRUE), 
    q3 = quantile(num.srvy, 0.75, na.rm = TRUE), 
    max = max(num.srvy, na.rm = TRUE), 
    NAs = sum(is.na(num.srvy))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

# NAs correspond to markets in survey A which are not found in survey C
```

\newpage

## (X) Distance to nearest town:
- *Distance to nearest town in km*

```{r towndist}

mrkts_master_noMtwara %>%
  summarise(
    min = min(town.dist, na.rm = TRUE), 
    q1 = quantile(town.dist, 0.25, na.rm = TRUE), 
    median = median(town.dist, na.rm = TRUE), 
    mean = mean(town.dist, na.rm = TRUE), 
    q3 = quantile(town.dist, 0.75, na.rm = TRUE), 
    max = max(town.dist, na.rm = TRUE), 
    NAs = sum(is.na(town.dist))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

distp1 <- ggplot(mrkts_master_noMtwara, aes(x=town.dist, group = town.type))+
  geom_histogram(aes(fill = town.type), alpha = 0.5, col = "black", boundary = 0)+
  labs(x = "Distance (km)",
       y = "Count")+
  theme(legend.position = "none")

distp2 <- ggplot(mrkts_master_noMtwara, aes(x = town.type, y=town.dist, group = town.type))+
  geom_boxplot(aes(fill = town.type),alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "", y = "Distance to nearest town")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

ggarrange(distp1, distp2, nrow = 1)

```

\newpage

## (2a) Small ruminants at market:

```{r anmlstotal}

# Sales per Market

mrkts_master_noMtwara %>%
  summarise(
    min = min(num.animals.all, na.rm = TRUE), 
    q1 = quantile(num.animals.all, 0.25, na.rm = TRUE), 
    median = median(num.animals.all, na.rm = TRUE), 
    mean = mean(num.animals.all, na.rm = TRUE), 
    q3 = quantile(num.animals.all, 0.75, na.rm = TRUE), 
    max = max(num.animals.all, na.rm = TRUE), 
    NAs = sum(is.na(num.animals.all))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

animalsp1 <- ggplot(mrkts_master_noMtwara, aes(x=num.animals.all))+
  geom_histogram(binwidth = 10, alpha = 0.5, col = "black", boundary = 0)+
  labs(x = "Small ruminants per market",
       y = "Count")
# 
# salesp2 <- ggplot(mrkts_master_noMtwara, aes(x = "SR sales", y=all.sales))+
#   geom_boxplot(fill = "grey",alpha = 0.5)+
#   geom_jitter(shape = 18, size = 2, width = 0.3)+
#   # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
#   labs(x = "", y = "Small ruminant sales per market")#+
#   # theme(axis.text.x = element_text(angle = 45, hjust = 1),
#   #       legend.position = "none")


mrkts_master_animals <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         prop.sheep.0to12,
         prop.sheep.adult, 
         prop.goat.0to12,
         prop.goat.adult) %>%
  gather(., key = "agegroup", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
  mutate(activity = ordered(agegroup, levels = c(
         "prop.sheep.0to12",
         "prop.sheep.adult",
         "prop.goat.0to12",
         "prop.goat.adult")))

mrkts_master_animals %>% 
  group_by(agegroup) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable()

mrktanimals1 <- ggplot(mrkts_master_animals, aes(x = agegroup, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "Age Group", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

mrktanimals2 <- ggplot(mrkts_master_noMtwara, aes(x=prop.animal.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Primary animal at market", y = "Count")


animalsp1
ggarrange(mrktanimals1, mrktanimals2, ncol = 1)

```
\newpage

## (2b) Small ruminant sales per market:

```{r mrktsales}

# Sales per Market

mrkts_master_noMtwara %>%
  summarise(
    min = min(all.sales, na.rm = TRUE), 
    q1 = quantile(all.sales, 0.25, na.rm = TRUE), 
    median = median(all.sales, na.rm = TRUE), 
    mean = mean(all.sales, na.rm = TRUE), 
    q3 = quantile(all.sales, 0.75, na.rm = TRUE), 
    max = max(all.sales, na.rm = TRUE), 
    NAs = sum(is.na(all.sales))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

salesp1 <- ggplot(mrkts_master_noMtwara, aes(x=all.sales))+
  geom_histogram(binwidth = 10, alpha = 0.5, col = "black", boundary = 0)+
  scale_x_continuous(breaks = seq(0,650,50), labels = seq(0,650,50))+
  labs(x = "Small ruminant sales per market",
       y = "Count")

salesp2 <- ggplot(mrkts_master_noMtwara, aes(x = "SR sales", y=all.sales))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "", y = "Small ruminant sales per market")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

ggarrange(salesp1, salesp2, nrow = 1)
```

\newpage

## (3) Other markets visited:

- *Mean visits to other markets per month, per actor*

```{r othermrkts}

# Other markets visited in past 1 month (mean per market)

mrkts_master_noMtwara %>%
  summarise(
    min = min(other.markets, na.rm = TRUE), 
    q1 = quantile(other.markets, 0.25, na.rm = TRUE), 
    median = median(other.markets, na.rm = TRUE), 
    mean = mean(other.markets, na.rm = TRUE), 
    q3 = quantile(other.markets, 0.75, na.rm = TRUE), 
    max = max(other.markets, na.rm = TRUE), 
    NAs = sum(is.na(other.markets))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

othermrktsp1 <- ggplot(mrkts_master_noMtwara, aes(x=other.markets))+
  geom_histogram(alpha = 0.5, col = "black", boundary = 0)+
  labs(x = "Other markets visited",
       y = "Count")


othermrktsp2 <- ggplot(mrkts_master_noMtwara, aes(x = "other.markets", y=other.markets))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "", y = "Other markets visited")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

ggarrange(othermrktsp1,othermrktsp2,nrow=1)
```


\newpage

## (4) Visits to this market:

- *Mean visits to this market per month, per actor*

```{r buysellmonth}

mrkts_master_noMtwara %>%
  summarise(
    min = min(buysell.month, na.rm = TRUE), 
    q1 = quantile(buysell.month, 0.25, na.rm = TRUE), 
    median = median(buysell.month, na.rm = TRUE), 
    mean = mean(buysell.month, na.rm = TRUE), 
    q3 = quantile(buysell.month, 0.75, na.rm = TRUE), 
    max = max(buysell.month, na.rm = TRUE), 
    NAs = sum(is.na(buysell.month))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

visits1 <- ggplot(mrkts_master_noMtwara, aes(x=buysell.month))+
  geom_histogram(alpha = 0.5, col = "black", boundary = 0)+
  labs(x = "Mean visits (buy/sell) at market per month",
       y = "Count")


visits2 <- ggplot(mrkts_master_noMtwara, aes(x = "Visits", y=buysell.month))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "", y = "Visits (buy/sell) at market per month")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

ggarrange(visits1, visits2, nrow = 1)
```

\newpage

## (5) Proportion traders at market
- *Proportion traders at market (self-id as "trader") *

```{r ptrader}

# Proportion trader at market:

mrkts_master_noMtwara %>% summarise(
    min = min(prop.trader, na.rm = TRUE), 
    q1 = quantile(prop.trader, 0.25, na.rm = TRUE), 
    median = median(prop.trader, na.rm = TRUE), 
    mean = mean(prop.trader, na.rm = TRUE), 
    q3 = quantile(prop.trader, 0.75, na.rm = TRUE), 
    max = max(prop.trader, na.rm = TRUE), 
    NAs = sum(is.na(prop.trader))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable()

trader1 <- ggplot(mrkts_master_noMtwara, aes(x=prop.trader))+
  geom_histogram(alpha = 0.5, col = "black", boundary = 0)+
  labs(x = "Proportion traders at market",
       y = "Count")


trader2 <- ggplot(mrkts_master_noMtwara, aes(x = "Trader", y=prop.trader))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "", y = "Proportion traders (self-id)")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

ggarrange(trader1, trader2, nrow = 1)

```


\newpage

## (6) Activities at the market

- Proportion actors at the market reporting activity types:
  - Selling
  - Buying
  - Trading
  - Brokering/Middleman
  - Other

```{r mrktactivity}

# mrkts_master_noMtwara %>%
#   select(prop.buy,
#          prop.sell,
#          prop.trade,
#          prop.middleman,
#          prop.otheractvty) %>%
#   summary()


mrkts_master_actvty <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         prop.buy,
         prop.sell,
         prop.trade,
         prop.middleman,
         prop.otheractvty) %>%
  gather(., key = "activity", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
  mutate(activity = ordered(activity, levels = c("prop.buy",
         "prop.sell",
         "prop.trade",
         "prop.middleman",
         "prop.otheractvty")))

mrkts_master_actvty %>% 
  group_by(activity) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable()

mrktacvty1 <- ggplot(mrkts_master_actvty, aes(x = activity, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "Market Activity", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

mrktacvty2 <- ggplot(mrkts_master_noMtwara, aes(x=prop.actvty.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Main market activity", y = "Count")

ggarrange(mrktacvty1, mrktacvty2, ncol = 1)
```

\newpage

## (7) Origins of animals sold at the market

- Proportion of actors bringing animals from different origin placetypes:
  - Village
  - Town
  - Market
  - Abattoir
  - Other

```{r, originplace}

# 
# mrkts_master_noMtwara %>%
#   select("origin.village",          
#          "origin.town" ,            
#          "origin.market" ,          
#          "origin.abattoir",
#          "origin.otherplace") %>%
#   summary()


mrkts_master_origplace <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         "origin.village",          
         "origin.town" ,            
         "origin.market" ,          
         "origin.abattoir",
         "origin.otherplace") %>%
  gather(., key = "placetype", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
  mutate(placetype = gsub("origin.", "", placetype),
         placetype = ordered(placetype, levels = c("village",          
         "town" ,            
         "market" ,          
         "abattoir",
         "otherplace")))

mrkts_master_origplace %>% 
  group_by(placetype) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable()

orig1 <- ggplot(mrkts_master_origplace, aes(x = placetype, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "Origin Placetype", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")


orig2 <- ggplot(mrkts_master_noMtwara, aes(x=origin.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Main origin placetype", y = "Count")

ggarrange(orig1, orig2, ncol = 1)

```


\newpage

## (8) Transport to market

- Proportion of actors using different types of tranasport to bring animals to market:
  - Foot
  - Vehicle
  - Cart
  - Other
  - Unknown

```{r, origintransport}
# 
# mrkts_master_noMtwara %>%
#   select("origin.foot",          
#          "origin.vehicle" ,            
#          "origin.cart" ,          
#          "origin.othertransport",
#          "origin.unknowntransport") %>%
#   summary()


mrkts_master_origtrans <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         "origin.foot",          
         "origin.vehicle" ,            
         "origin.cart" ,          
         "origin.othertransport",
         "origin.unknowntransport") %>%
  gather(., key = "transtype", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
  mutate(
         transtype = ordered(transtype, levels = c("origin.foot",         
         "origin.vehicle" ,            
         "origin.cart" ,          
         "origin.othertransport",
         "origin.unknowntransport")))

mrkts_master_origtrans %>% 
  group_by(transtype) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

origtrans1 <- ggplot(mrkts_master_origtrans, aes(x = transtype, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "Origin Transport-type", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

origtrans2 <- ggplot(mrkts_master_noMtwara, aes(x=origin.transport.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Main origin transport", y = "Count")

ggarrange(origtrans1, origtrans2, ncol = 1)

```


\newpage

## (9) Destinations of animals bought at market
- Proportion of actors taking animals to different destination placetypes:


```{r, destplace}
# 
# mrkts_master_noMtwara %>%
#   select("dest.village",          
#          "dest.town" ,            
#          "dest.market" ,          
#          "dest.abattoir",
#          "dest.otherplace") %>%
#   summary()

mrkts_master_distplace <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         "dest.village",          
         "dest.town" ,            
         "dest.market" ,          
         "dest.abattoir",
         "dest.otherplace") %>%
  gather(., key = "placetype", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
   mutate(placetype = gsub("dest.", "", placetype),
         placetype = ordered(placetype, levels = c("village",          
         "town" ,            
         "market" ,          
         "abattoir",
         "otherplace")))

mrkts_master_distplace %>% 
  group_by(placetype) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

dest1 <- ggplot(mrkts_master_distplace, aes(x = placetype, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "dest Placetype", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

dest2 <- ggplot(mrkts_master_noMtwara, aes(x=dest.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Main destination placetype", y = "Count")

ggarrange(dest1, dest2, ncol = 1)
```

\newpage

### (9ii) Correlation between origin and destination placetype

- *Correlations between proportion origins and proportion destinations at each market*

```{r placetypecor}

placetype_cor <- left_join(
  mrkts_master_origplace,
  mrkts_master_distplace %>% rename(dest.proportion = proportion),
  by = c("fid", "market.final", "placetype")
)

ggplot(placetype_cor, aes(x=proportion, y = dest.proportion))+
  geom_point()+
  facet_wrap(~placetype, scales = "free")+
  labs(x = "Origin placetype proportion", y = "Destination placetype proportion")
```


\newpage

## (10) Transport from market

- Proportion of actors using different types of transport to take animals to market:
  - Foot
  - Vehicle
  - Cart
  - Other
  - Unknown

```{r, desttransport}

# mrkts_master_noMtwara %>%
#   select("dest.foot",          
#          "dest.vehicle" ,            
#          "dest.cart" ,          
#          "dest.othertransport",
#          "dest.unknowntransport") %>%
#   summary()


mrkts_master_desttrans <- mrkts_master_noMtwara %>%
  select(fid, 
         market.final, 
         "dest.foot",          
         "dest.vehicle" ,            
         "dest.cart" ,          
         "dest.othertransport",
         "dest.unknowntransport") %>%
  gather(., key = "transtype", value = "proportion", -c(fid,market.final)) %>% 
  ungroup() %>%
  mutate(
         transtype = ordered(transtype, levels = c("dest.foot",          
         "dest.vehicle" ,            
         "dest.cart" ,          
         "dest.othertransport",
         "dest.unknowntransport")))


mrkts_master_desttrans %>% 
  group_by(transtype) %>%
  summarise(
    min = min(proportion, na.rm = TRUE), 
    q1 = quantile(proportion, 0.25, na.rm = TRUE), 
    median = median(proportion, na.rm = TRUE), 
    mean = mean(proportion, na.rm = TRUE), 
    q3 = quantile(proportion, 0.75, na.rm = TRUE), 
    max = max(proportion, na.rm = TRUE), 
    NAs = sum(is.na(proportion))
  ) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() 

desttrans1 <- ggplot(mrkts_master_desttrans, aes(x = transtype, y=proportion))+
  geom_boxplot(fill = "grey",alpha = 0.5)+
  geom_jitter(shape = 18, size = 2, width = 0.3)+
  # stat_summary(fun.data = give.n, geom = "text", fun.y = max)+
  labs(x = "dest transport", y = "Proportion")#+
  # theme(axis.text.x = element_text(angle = 45, hjust = 1),
  #       legend.position = "none")

desttrans2 <- ggplot(mrkts_master_noMtwara, aes(x=dest.transport.main))+
  geom_histogram(stat = "count", alpha = 0.5, col = "black")+
  labs(x = "Main destination transport", y = "Count")

ggarrange(desttrans1, desttrans2, ncol = 1)

```
