---
title: "marketC_mapping"
output: html_document
date: "2024-01-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = F}

library(sf)
library(here)
library(tidyverse)
library(RColorBrewer)
library(lwgeom)
library(ggpubr)

```

```{r theme, include = F}
custom_theme <- theme_bw() + 
  theme(text = element_text(family = "Times New Roman", size = 10))
theme_set(custom_theme)

tanzania_pal <- rep(brewer.pal(9,"Pastel1"),times=4)
market_pal <- c(brewer.pal(8, "Dark2"), "#FFA500", "#6A3D9A", "#33A02C", "#FFD700", "#1E90FF")
```


# Mapping Market Survey C Locations

- Load in market survey C data (following initial string cleaning)
    - `r `"data/tanzania_data/mrkta_gps_tanzania_CLEAN.csv"`
- Load in clean geomatched market survey A data.
    - `r `"data/tanzania_data/mrkta_gps_tanzania_CLEAN.csv"`
- Load Tanzania shapefile with ward boundaries
    - `r `"data/shapefiles/tza_admbnda_adm3_20181019.shp"`
    - Source <https://data.humdata.org/dataset/cod-ab-tza?> (ADM L3)

```{r data, include = T, warning = F, echo = F}

# Load Tanzania Shapefile:
# tanzania_shp <- st_read(here("data/shapefiles/Districts and TC as 2020.shp")) # with district boundaries
tregs_shp <- st_read(here("data/shapefiles/tza_admbnda_adm1_20181019.shp")) %>% # with region boundaries
   rename(
    "Country_N"=ADM0_EN,    
    "Country_NSw" = ADM0_SW,
    "Country_C"=ADM0_PCODE,
    "Region_Nam" = ADM1_EN,
    "Region_Cod" = ADM1_PCODE,
  )

# tdists_shp <- st_read(here("data/shapefiles/tza_admbnda_adm2_20181019.shp")) # with district boundaries
twards_shp <- st_read(here("data/shapefiles/tza_admbnda_adm3_20181019.shp")) %>% # with ward boundaries
    rename(
    "Country_N"=ADM0_EN,    
    "Country_NSw" = ADM0_SW,
    "Country_C"=ADM0_PCODE,
    "Region_Nam" = ADM1_EN,
    "Region_Cod" = ADM1_PCODE,
    "District_N" = ADM2_EN,
    "District_C" = ADM2_PCODE,
    "Ward_Name"=ADM3_EN,
    "Ward_Code"= ADM3_PCODE
  )

# Market A location data:
mrkta_gps <- read_csv(file = here("data/data-cleaning_data/mrkta_gps_tanzania_final.csv"))
mrkta_gps_join <- read_csv(file = here("data/data-cleaning_data/mrkta_gps_tanzania_manual+geomatch.csv")) %>%
  rename(ward.code.manual = ward.code,
         ward.name.manual = ward.name,
         village.manual = village, 
         market.name.manual = market.name.corrected
         )

# Market C location data:
# mrktc_clean3 <- read_csv(file = here("data/data-cleaning_data/mrktc_info_clean3-1.csv"))
mrktc_gps <- read_csv(file = here("data/tanzania_data/mrktc_gps_tanzania_CLEAN1.csv")) %>%
  rename(ward.code.manual = ward.code.3A,
         ward.name.manual = ward.name.3A,
         village.manual = village.3A, 
         market.name.manual = market.name.3A
         )

mrktc_gps_raw <- read_csv(file = here(
  "data/data-cleaning_data/mrktc_generalinfo_tanzania_CLEAN.csv"
)) %>%
  select(
    fid,
    date,
    date.end,
    date.of.interview,
    country,
    region.code.raw = district.region.code,
    region.name.raw = district.region.name,
    ward.code.raw = ward.code,
    ward.name.raw = ward.name,
    village.raw = village,
    market.name.raw = market.name,
    ward.code.manual = ward.code.3A,
    ward.name.manual = ward.name.3A,
    village.manual = village.3A,
    market.name.manual = market.name.3A,
    gps.coordinates.of.the.market,
    unique.row.identifier.uuid.
  )

```


## Market A Map
- Market A data, matched to Tanzania shapefile region-district-ward locations
- See `mrktA_mapping.Rmd`

```{r mrktaMap}
# convert mrkta location data to mapping format & map manually cleaned data:

mrkta_mapdata <- mrkta_gps %>% 
  mutate(lat = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 1],
         long = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 2]) %>% 
  filter(!is.na(lat), !is.na(long))

# for now ignore rows which have na in lat or long:
mrkta_sf <- st_as_sf(mrkta_mapdata, coords = c("long","lat"),  crs = 4326)

mrkta_map <- ggplot() +
  geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  geom_sf(data = mrkta_sf, aes(col = region.geomatch.final), size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+
  labs(title = "Market survey A: survey locations", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrkta_map

# Map of market survey locations coloured by region (consistency with Tanzania shapefile)

Regions_Amanual <- mrkta_sf %>% pull(region.geomatch.final) %>% unique() %>% str_to_title()

mrkta_mapByReg <- ggplot() +
  geom_sf(data = tregs_shp, fill = "grey", alpha = 0.5, linewidth = 0.1) +
  geom_sf(data = tregs_shp %>% filter(Region_Nam %in% Regions_Amanual), aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(market_pal,0.5), guide = "none")+
  geom_sf(data = mrkta_sf, aes(col = region.geomatch.final), size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+
  labs(title = "Market survey A: survey locations (coloured by stringRegion)", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrkta_mapByReg

# mrkta-manual string-location data is consistent with tanzania shapefile for REGION of origin. 

# mrkta-manual Descriptive stats:
# mrkta_gps %>% group_by(district.region.name) %>% count()
# mrkta_gps %>% group_by(ward.name) %>% count()
# mrkta_gps %>% group_by(ward.name) %>% count() %>% filter(n>1)
# mrkta_gps %>% group_by(ward.name) %>% count() %>% filter(n>1)
# mrkta_gps %>% group_by(district.region.name, ward.name) %>% count() %>% filter(n>1) # mamba only appears in ward.name unique list
# mrkta_gps %>% filter(ward.name == "mamba")
# mrkta_gps %>% group_by(district.region.name, ward.name, village) %>% count() 
# mrkta_gps %>% group_by(district.region.name, ward.name, village, market.name.corrected) %>% count() 

```

## Market C Map (1)
- Location of market C surveys, overlaid on market A survey locations

```{r, mrktcMap_manual-cleaning}

mrktc_mapdata <- mrktc_gps %>% 
  mutate(lat = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 1],
         long = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 2]) %>% 
  arrange(gps.coordinates.of.the.market) %>% 
  filter(!is.na(lat), !is.na(long))

# for now ignore rows which have na in lat or long:
mrktc_sf <- st_as_sf(mrktc_mapdata, coords = c("long","lat"),  crs = 4326) 

mrktC_map <- ggplot() +
  geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  geom_sf(data = mrktc_sf, aes(col = district.region.name), size = 1)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+ 
  labs(title = "Market survey C: survey locations", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrktC_map

mrktCA_map <- ggplot() +
   geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   geom_sf(data = mrkta_sf, aes(col = region.geomatch.final), alpha = 0.5, size = 3)+
   geom_sf(data = mrktc_sf, aes(col = district.region.name),  shape = 17, size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
   scale_colour_manual(values = market_pal)+
   coord_sf()+
   labs(title = "Market Survey A-geoamtched (circles) and C-manual (triangles) data",
        fill = "Tanzania region",
        col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")
 
mrktCA_map

```


```{r datacheck}
# Check consistency between markets in mrkta_gps and mrktc_gps_raw (.manual)
mrkta_gps %>% distinct(region.geomatch.final, ward.geomatch.final, market.manual.final)
mrktc_gps_raw %>% distinct(region.name.raw, ward.name.manual, market.name.manual)

```
1) Market survey C - match to market survey A 
- Use market survey C gps locations to link to market survey A geo-matched data.
 - Each market survey C entry should be linked to a market identified in market survey A data.
 - Compare consistency between raw/manual survey C locations and A-linked survey locations.
 - Compare consistency between raw/manual survey C locations, overlaid on survey A locations
 - Compare consistently between A-linked survey C locations overlaid on survey A location (should be perfect match)


```{r mrktc_linkA}

mrktc_gps

mrktc_mapdata %>%
  mutate(mrktaID = st_nearest_feature(mrktc_sf, mrkta_sf)) %>% 
  left_join(
    mrkta_mapdata %>%
      mutate(mrktaID = 1:nrow(.)) %>%
      select(
        mrktaID,
        "district.region.code.A" = "district.region.code",
        "district.region.name.A" = "district.region.name",
        "ward.code.A" = "ward.code",
        "ward.name.A" = "ward.name" ,
        "village.A" = "village",
        "market.name.A" = "market.name.corrected"
      ),
    by = c("mrktaID"))


```
 
 
 
 
 

2) On a region-by-region basis:
- Use c-geomatchA locations and group by survey date. 
- All surveys for a given market should be completed on the same day
- For surveys which seem to be inconsistent check the original mrktc location names etc. 











# Review Location Data

```{r checkData}
mrktc_gps %>% colnames()

# unique region-ward combinations in market C survey data
mrktc_manualNames <- mrktc_gps %>% select(district.region.name, ward.name.manual) %>% distinct() %>% arrange(district.region.name, ward.name.manual)

# Are these the same as the survey A manual region-ward combinations ? (they should be)
mrkta_manualNames <- mrkta_gps_join %>% select(district.region.name, ward.name.manual) %>% distinct() %>% arrange(district.region.name, ward.name.manual)

print(paste("market C survey has ", nrow(mrktc_manualNames), "unique region-ward locations.",
            "market A survey has ", nrow(mrkta_manualNames), "unique region-ward locations."))

anti_join(mrkta_manualNames, mrktc_manualNames)
anti_join(mrktc_manualNames, mrkta_manualNames)


# unique region-ward combinations in market C survey data
mrktc_manualNames <- mrktc_gps %>% select(district.region.name, ward.name.manual, market.name.manual) %>% distinct() %>% arrange(district.region.name, ward.name.manual, market.name.manual)

# Are these the same as the survey A manual region-ward combinations ? (they should be)
mrkta_manualNames <- mrkta_gps_join %>% select(district.region.name, ward.name.manual,market.name.manual) %>% distinct() %>% arrange(district.region.name, ward.name.manual,market.name.manual)

print(paste("market C survey has ", nrow(mrktc_manualNames), "unique region-ward locations.",
            "market A survey has ", nrow(mrkta_manualNames), "unique region-ward locations."))

anti_join(mrkta_manualNames, mrktc_manualNames)
anti_join(mrktc_manualNames, mrkta_manualNames)


# Join geomatched locatiion data to mrkt survey C by the manually matched location data (equal between A and C)
mrktc_gps_geomatch <- mrktc_gps %>% 
  left_join(mrkta_gps_join %>% 
              select(district.region.name, ward.name.manual, market.name.manual, reg.ward.mrkt.final, ends_with("geomatch")),
            by = c("district.region.name", "ward.name.manual","market.name.manual"))

# what to do about unmatched rows: anti_join(mrktc_manualNames, mrkta_manualNames) ??


# In geomatched data, are unique markets associated with 1 survey date?
mrktc_gps_geomatch %>% distinct(region.name.geomatch, ward.name.geomatch, market.name.manual)
mrktc_gps_geomatch %>% distinct(reg.ward.mrkt.final)

mrktc_gps_geomatch %>% group_by(reg.ward.mrkt.final, date) %>% count() %>% View()

# for markets associated with more than 1 date, check full mrktc_info data? Use count data to identify typos (where only 1 survey completed on that date, so probable data entry error)

```




####################################



# Market Maps (1) : Manually Cleaned

## Market A Map - Manually Cleaned.
- Market A string-location data manually cleaned (see : `r source(here("data-cleaning_scripts/mrkta_cleaning-script.Rmd"))` )
- Market A map survey locations data consistent with regional tanzania map for all surveys *except* survey in Ruvuma (yellow), labelled as Rukwa. 
```{r mrktaMap}
# convert mrkta location data to mapping format & map manually cleaned data:

mrkta_mapdata <- mrkta_gps %>% 
  mutate(lat = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 1],
         long = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 2]) %>% 
  filter(!is.na(lat), !is.na(long))

# for now ignore rows which have na in lat or long:
mrkta_sf <- st_as_sf(mrkta_mapdata, coords = c("long","lat"),  crs = 4326)

mrkta_map <- ggplot() +
  geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  geom_sf(data = mrkta_sf, aes(col = district.region.name), size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+
  labs(title = "Market survey A: survey locations", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrkta_map

# Map of market survey locations coloured by region (consistency with Tanzania shapefile)

Regions_Amanual <- mrkta_sf %>% pull(district.region.name) %>% unique() %>% str_to_title()

mrkta_mapByReg <- ggplot() +
  geom_sf(data = tregs_shp, fill = "grey", alpha = 0.5, linewidth = 0.1) +
  geom_sf(data = tregs_shp %>% filter(Region_Nam %in% Regions_Amanual), aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(market_pal,0.5), guide = "none")+
  geom_sf(data = mrkta_sf, aes(col = district.region.name), size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+
  labs(title = "Market survey A: survey locations (coloured by stringRegion)", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrkta_mapByReg

# mrkta-manual string-location data is consistent with tanzania shapefile for REGION of origin. 

# mrkta-manual Descriptive stats:
# mrkta_gps %>% group_by(district.region.name) %>% count()
# mrkta_gps %>% group_by(ward.name) %>% count()
# mrkta_gps %>% group_by(ward.name) %>% count() %>% filter(n>1)
# mrkta_gps %>% group_by(ward.name) %>% count() %>% filter(n>1)
# mrkta_gps %>% group_by(district.region.name, ward.name) %>% count() %>% filter(n>1) # mamba only appears in ward.name unique list
# mrkta_gps %>% filter(ward.name == "mamba")
# mrkta_gps %>% group_by(district.region.name, ward.name, village) %>% count() 
# mrkta_gps %>% group_by(district.region.name, ward.name, village, market.name.corrected) %>% count() 

```

## Market C Map - manually cleaned. 
- Manual cleaning, market C cross-referenced with market A (not geo-matched)

```{r, mrktcMap_manual-cleaning}

mrktc_mapdata <- mrktc_gps %>% 
  mutate(lat = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 1],
         long = str_split(`gps.coordinates.of.the.market`, "\\s", simplify = TRUE)[, 2]) %>% 
  arrange(gps.coordinates.of.the.market) %>% 
  filter(!is.na(lat), !is.na(long))

# for now ignore rows which have na in lat or long:
mrktc_sf <- st_as_sf(mrktc_mapdata, coords = c("long","lat"),  crs = 4326) 

mrktC_map <- ggplot() +
  geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
  scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  geom_sf(data = mrktc_sf, aes(col = district.region.name), size = 1)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
  scale_colour_manual(values = market_pal)+
  coord_sf()+ 
  labs(title = "Market survey C: survey locations", 
       fill = "Tanzania region",
       col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")

mrktC_map

mrktC3andA_map <- ggplot() +
   geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   geom_sf(data = mrkta_sf, aes(col = district.region.name), alpha = 0.5, size = 3)+
   geom_sf(data = mrktc_sf, aes(col = district.region.name),  shape = 17, size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
   scale_colour_manual(values = market_pal)+
   coord_sf()+
   labs(title = "Market Survey A (circles) and C (triangles) - manually cleaned location data",
        fill = "Tanzania region",
        col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")
 
mrktC3andA_map

```

# Market C Map 2 - market C geo-matched to market A
- For each Market Survey C location, match to the closest Market Survey A location

```{r mrktcMap_C-A-matched}

mrktCtoAmatch <- mrktc_mapdata %>%
  mutate(mrktaID = st_nearest_feature(mrktc_sf, mrkta_sf)) %>% 
  left_join(
    mrkta_mapdata %>%
      mutate(mrktaID = 1:nrow(.)) %>%
      select(
        mrktaID,
        "district.region.code.A" = "district.region.code",
        "district.region.name.A" = "district.region.name",
        "ward.code.A" = "ward.code",
        "ward.name.A" = "ward.name" ,
        "village.A" = "village",
        "market.name.A" = "market.name.corrected"
      ),
    by = c("mrktaID"))


mrktCtoAmatch_gps <- mrktCtoAmatch %>%
  select(
      country,
      ends_with(".A"),
      lat,
      long,
      gps.coordinates.of.the.market
    )
  
mrktCtoAmatch_sf <- st_as_sf(mrktCtoAmatch_gps, coords = c("long","lat"),  crs = 4326)

mrktCAmatched_map <- ggplot() +
   geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   geom_sf(data = mrkta_sf, aes(col = district.region.name), alpha = 0.5, size = 3)+
   geom_sf(data = mrktCtoAmatch_sf, aes(col = district.region.name.A),  shape = 17, size = 1.5)+
  geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+
   scale_colour_manual(values = market_pal)+
   coord_sf()+
   labs(title = "Market Survey A (circles) and C (triangles) - market locations",
        fill = "Tanzania region",
        col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")
 
mrktCAmatched_map


###################
# PLOTS BY REGION #
###################
# mrkta_sf <- mrkta_sf %>% mutate(mrktID = paste(ward.name,village,market.name.corrected, sep = "-"))
# mrktCtoAmatch_sf <- mrktCtoAmatch_sf %>% mutate(mrktID = paste(ward.name.A,village.A,market.name.A, sep = "-"))
# 
# districts <- mrktc_sf %>% distinct(district.region.name) %>% pull()
# Districts <- str_to_title(districts)
# 
# map_plots <- list()
# for (i in 1:length(districts)) {
#   
#   District_i <- Districts[i]
#   district_i <- districts[i]
#   
#   map_plots[[i]] <- ggplot() +
#     geom_sf(data = tregs_shp %>% filter(Region_Nam == District_i), fill = NA) +
#     geom_sf(data = mrkta_sf %>% filter(district.region.name == district_i), aes(col = mrktID), alpha = 0.5, size = 3)+
#     geom_sf(data = mrktCtoAmatch_sf %>% filter(district.region.name.A == district_i), aes(col = mrktID), shape = 17, size = 1)+
#     scale_colour_brewer(palette = "Paired")+
#     facet_wrap(~district.region.name)+
#     coord_sf()+
#     theme_bw()
# }
# 
# map_plots[[1]] <- ggplot() +
#   geom_sf(data = tregs_shp %>% filter(Region_Nam == "Mtwara"), fill = NA) +
#   geom_sf(data = mrkta_sf %>% filter(district.region.name == "mtwara"), col = "black", alpha = 0.5, size = 3)+
#   geom_sf(data = mrktCtoAmatch_sf %>% filter(district.region.name.A == "mtwara"), col = "red", shape = 17, size = 1)+
#   # scale_colour_brewer(palette = "Paired")+
#   facet_wrap(~district.region.name)+
#   coord_sf()+
#   theme_bw()
# 
# map_plots[[1]]; map_plots[[2]]; map_plots[[3]]; map_plots[[4]]; map_plots[[5]]; map_plots[[6]]; map_plots[[7]]; 
# map_plots[[8]]; map_plots[[9]]; map_plots[[10]]; map_plots[[11]]

```
# Market Maps (2): Geo-matched Locations


# Market A Map 2.1: 
- Market A geo-matched to Tanzania Administrative Levels

```{r mrktcMap_A-Ward-matched}
sf_use_s2(FALSE)
mrkta_sf2 <- st_transform(mrkta_sf, crs = st_crs(twards_shp))

twards_shp <- twards_shp %>%
  mutate("District_N" = tolower(gsub(" ", ".", District_N)),
        "Region_Nam" = tolower(gsub(" ",".",Region_Nam)),
        "Ward_Name" = tolower(gsub(" ",".",Ward_Name))
        )

mrktAtwards_match <- mrkta_mapdata %>%
  mutate(twardID = st_nearest_feature(mrkta_sf2,twards_shp)) %>% 
  left_join(
    twards_shp %>%
      mutate(twardID = 1:nrow(.)) %>%
      select(
        twardID,
        "region.name.twards" = "Region_Nam",
        "district.name.twards" = "District_N",
        "ward.name.twards" = "Ward_Name" ,
      ),
    by = c("twardID"))
# mrktCtwards_match %>% group_by(region.name.twards, district.name.twards) %>% count() %>% View()


mrktAtwards_match_gps <- mrktAtwards_match %>%
  select(
      country,
      region.name.twards,
      district.name.twards,
      ward.name.twards,
      district.region.name.A = district.region.name,
      ward.name.A = ward.name,
      village.A = village,
      market.name.A = market.name.corrected,
      lat,
      long,
      gps.coordinates.of.the.market
    ) %>% 
  mutate(region.district.name.twards = paste(region.name.twards, district.name.twards, sep = "-"))

mrktAtwards_match_sf <- st_as_sf(mrktAtwards_match_gps, coords = c("long","lat"),  crs = 4326)


##################################
# Geo-matched Map, check Regions #
##################################

## Region: id regions with surveyed markets:
regions <- mrktAtwards_match_sf %>% distinct(region.name.twards) %>% pull()
Regions <- str_to_title(regions)

mrktAtwards_match_map <- ggplot() +
  geom_sf(data = tregs_shp, fill = NA, linewidth = 0.1) +

   geom_sf(data = twards_shp %>% filter(Region_Nam %in% regions), aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   # geom_sf(data = mrkta_sf, aes(col = district.region.name), alpha = 0.5, size = 3)+
  geom_sf(data = mrktAtwards_match_sf, aes(col = region.name.twards), alpha = 0.5, size = 3)+
  geom_sf(data = mrktAtwards_match_sf, aes(col = district.region.name.A),  shape = 17, size = 1.5)+
   scale_colour_manual(values = rep(market_pal,9))+
   coord_sf()+
   labs(title = "Market Survey A locations: ward-matched (circle) and manual (triangle)",
        fill = "Tanzania region",
        col = "Market region")+
  #theme(legend.position = "none") #+
  theme(legend.position = "bottom", legend.box = "horizontal")
 
mrktAtwards_match_map

#########################################
# Geo-matched Map, check Ward by Region #
#########################################

## Region: id wards with surveyed markets:
wardlist <- mrktAtwards_match %>% select(ward.name.twards) %>% distinct() %>% pull()

map_plots <- list()
for (i in 1:length(regions)) {

  Region_i <- Regions[i]
  region_i <- regions[i]
  
  # For region (i) id wards with surveyed markets according to geo-matched data 
  wardlist_i <- mrktAtwards_match %>% 
    filter(region.name.twards == region_i) %>% 
    select(ward.name.twards) %>% 
    distinct() %>% pull()
  
  map_plots[[i]] <- ggplot() +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i), fill = NA) +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i,
                                         Ward_Name %in% wardlist_i), 
            aes(fill = Ward_Name, alpha = 0.5)) +

    geom_sf(data = mrktAtwards_match_sf %>% filter(region.name.twards == region_i),
            aes(col = ward.name.twards),  alpha = 0.5, size = 3)+
    # geom_sf(data = mrktAtwards_match_sf %>% filter(region.name.twards == region_i), 
    #         aes(col = ward.name.A),  shape = 17, size = 1.5)+
    # geom_sf(data = mrktCtwards_match_sf%>% filter(region.name.twards == region_i), aes(col = ward.name.3A),  shape = 17, size = 1.5)+
    scale_fill_manual(values = rep(market_pal,10))+    
    scale_colour_manual(values = rep(market_pal,10))+
    facet_wrap(~region.name.twards)+
    coord_sf()+
    theme(legend.position = "bottom")
}

map_plots[[1]]; map_plots[[2]]; map_plots[[3]]; map_plots[[4]]; map_plots[[5]]; map_plots[[6]]; map_plots[[7]];
map_plots[[8]]; map_plots[[9]]; map_plots[[10]]; map_plots[[11]]; map_plots[[12]]; map_plots[[13]]
```

# Market C Map 2.2: 
- Market C geo-matched to Tanzania Administrative Levels


```{r mrktcMap_C-geomatched}
sf_use_s2(FALSE)
mrktc_sf2 <- st_transform(mrktc_sf, crs = st_crs(twards_shp))

twards_shp <- twards_shp %>%
  mutate("District_N" = tolower(gsub(" ", ".", District_N)),
        "Region_Nam" = tolower(gsub(" ",".",Region_Nam)),
        "Ward_Name" = tolower(gsub(" ",".",Ward_Name))
        )

mrktCtwards_match <- mrktc_mapdata %>%
  mutate(twardID = st_nearest_feature(mrktc_sf2,twards_shp)) %>% 
  left_join(
    twards_shp %>%
      mutate(twardID = 1:nrow(.)) %>%
      select(
        twardID,
        "region.name.twards" = "Region_Nam",
        "district.name.twards" = "District_N",
        "ward.name.twards" = "Ward_Name" ,
      ),
    by = c("twardID"))
# mrktCtwards_match %>% group_by(region.name.twards, district.name.twards) %>% count() %>% View()

mrktCtwards_match_gps <- mrktCtwards_match %>%
  select(
      country,
      region.name.twards,
      district.name.twards,
      ward.name.twards,
      district.region.name.3A = district.region.name,
      ward.name.3A,
      village.3A,
      market.name.3A,
      lat,
      long,
      gps.coordinates.of.the.market
    ) %>% 
  mutate(region.district.name.twards = paste(region.name.twards, district.name.twards, sep = "-"))
  
mrktCtwards_match_sf <- st_as_sf(mrktCtwards_match_gps, coords = c("long","lat"),  crs = 4326)


##################################
# Geo-matched Map, check Regions #
##################################

## Region: id regions with surveyed markets:
regions <- mrktCtwards_match_sf %>% distinct(region.name.twards) %>% pull()
Regions <- str_to_title(regions)

mrktCtwards_match_sf <- st_as_sf(mrktCtwards_match_gps, coords = c("long","lat"),  crs = 4326)

mrktCtwards_match_map <- ggplot() +
  geom_sf(data = tregs_shp, fill = NA, linewidth = 0.1) +

   geom_sf(data = twards_shp %>% filter(Region_Nam %in% regions), aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   # geom_sf(data = mrktc_sf, aes(col = district.region.name), alpha = 0.5, size = 3)+
  geom_sf(data = mrktCtwards_match_sf, aes(col = region.name.twards), alpha = 0.5, size = 3)+
  geom_sf(data = mrktCtwards_match_sf, aes(col = district.region.name.3A),  shape = 17, size = 1.5)+
   scale_colour_manual(values = rep(market_pal,9))+
   coord_sf()+
   labs(title = "Market Survey C locations: ward-matched (circle) and manual (triangle)",
        fill = "Tanzania region",
        col = "Market region")+
  #theme(legend.position = "none") #+
  theme(legend.position = "bottom", legend.box = "horizontal")
 
mrktCtwards_match_map
```

```{r, mrktcMap_C-geomatchedWards}
#########################################
# Geo-matched Map, check Ward by Region #
#########################################

## Region: id wards with surveyed markets:
wardlist <- mrktCtwards_match %>% select(ward.name.twards) %>% distinct() %>% pull()

map_plots <- list()
for (i in 1:length(regions)) {

  Region_i <- Regions[i]
  region_i <- regions[i]
  
  # For region (i) id wards with surveyed markets according to geo-matched data 
  wardlist_i <- mrktCtwards_match %>% 
    filter(region.name.twards == region_i) %>% 
    select(ward.name.twards) %>% 
    distinct() %>% pull()
  
  map_plots[[i]] <- ggplot() +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i), fill = NA) +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i,
                                         Ward_Name %in% wardlist_i), 
            aes(fill = Ward_Name, alpha = 0.5)) +

    geom_sf(data = mrktCtwards_match_sf %>% filter(region.name.twards == region_i), aes(col = ward.name.twards),  alpha = 0.5, size = 3)+
    # geom_sf(data = mrktCtwards_match_sf %>% filter(region.name.twards == region_i), aes(col = ward.name.3A),  shape = 17, size = 1.5)+
  #   geom_sf(data = mrktCtwards_match_sf %>% filter(region.name.twards == region_i)%>% filter(region.name.twards == region_i), aes(col = region.name.twards), alpha = 0.5, size = 3)+
  # geom_sf(data = mrktCtwards_match_sf %>% filter(region.name.twards == region_i), aes(col = district.region.name.3A),  shape = 17, size = 1.5)+
    scale_fill_manual(values = rep(market_pal,10))+    
    scale_colour_manual(values = rep(market_pal,10))+
    facet_wrap(~region.name.twards)+
    coord_sf()+
    theme(legend.position = "bottom")
}

map_plots[[1]]; map_plots[[2]]; map_plots[[3]]; map_plots[[4]]; map_plots[[5]]; map_plots[[6]]; map_plots[[7]];
map_plots[[8]]; map_plots[[9]]; map_plots[[10]]; map_plots[[11]]; map_plots[[12]]; map_plots[[13]]
```


```{r mrktcMap_C+A}

##################################
# Geo-matched Map, check Regions #
##################################

## Region: id regions with surveyed markets:
regions <- mrktCtwards_match_sf %>% distinct(region.name.twards) %>% pull()
Regions <- str_to_title(regions)

mrktCtwards_match_sf <- st_as_sf(mrktCtwards_match_gps, coords = c("long","lat"),  crs = 4326)

mrktAC_geomatch_map <- ggplot() +
  geom_sf(data = tregs_shp, fill = NA, linewidth = 0.1) +

   geom_sf(data = twards_shp %>% filter(Region_Nam %in% regions), aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
   # geom_sf(data = mrktc_sf, aes(col = district.region.name), alpha = 0.5, size = 3)+
  geom_sf(data = mrktAtwards_match_sf, aes(col = region.name.twards), alpha = 0.5, size = 3)+
  geom_sf(data = mrktCtwards_match_sf, aes(col = region.name.twards),  shape = 17, size = 1.5)+
   scale_colour_manual(values = rep(market_pal,9))+
   coord_sf()+
   labs(title = "Geo-matched locations: Market A (circle) and Market C (triangle)",
        fill = "Tanzania region",
        col = "Market region")+
  #theme(legend.position = "none") #+
  theme(legend.position = "bottom", legend.box = "horizontal")
 
mrktAC_geomatch_map

```

```{r mrktcMap_C-Ward-matched2}

##################
# PLOTS BY WARD #
##################

map_plots <- list()
for (i in 1:length(regions)) {

  Region_i <- Regions[i]
  region_i <- regions[i]
  wardlist_i <- mrktCtwards_match %>% filter(region.name.twards == region_i) %>% select(ward.name.twards) %>% distinct() %>% pull()
  
  map_plots[[i]] <- ggplot() +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i), fill = NA) +
    geom_sf(data = twards_shp %>% filter(Region_Nam == region_i,
                                         Ward_Name %in% wardlist_i), aes(fill = Ward_Name, alpha = 0.5)) +

    geom_sf(data = mrktAtwards_match_sf%>% filter(region.name.twards == region_i), aes(col = ward.name.twards),  alpha = 0.5, size = 3)+
    geom_sf(data = mrktCtwards_match_sf%>% filter(region.name.twards == region_i), aes(col = ward.name.twards),  shape = 17, size = 1.5)+
    scale_fill_manual(values = rep(market_pal,10))+    
    scale_colour_manual(values = rep(market_pal,10))+
    facet_wrap(~region.name.twards)+
    coord_sf()+
    theme(legend.position = "bottom")
}

map_plots[[1]]; map_plots[[2]]; map_plots[[3]]; map_plots[[4]]; map_plots[[5]]; map_plots[[6]]; map_plots[[7]];
map_plots[[8]]; map_plots[[9]]; map_plots[[10]]; map_plots[[11]]; map_plots[[12]]; map_plots[[13]]

```

# Maps 3: C to geomathced A


```{r }

mrktCtoAmatch2 <- mrktCtwards_match_gps %>%
  mutate(mrktaID = st_nearest_feature(mrktCtwards_match_sf, mrktAtwards_match_sf)) %>% 
  left_join(
    mrktAtwards_match_gps %>%
      mutate(mrktaID = 1:nrow(.)) %>%
      select(
        mrktaID,
        # district.region.name.A,
        # ward.name.A,
        # village.A,
        # market.name.A,  
        "region.name.twards.A"=region.name.twards,
       "district.name.twards.A"= district.name.twards,
        "ward.name.twards.A"=ward.name.twards
      ),
    by = c("mrktaID"))


mrktCtoAmatch_gps2 <- mrktCtoAmatch2 %>%
  select(
      country,
      ends_with("twards.A"),
      lat,
      long,
      gps.coordinates.of.the.market
    )
  
mrktCtoAmatch_sf2 <- st_as_sf(mrktCtoAmatch_gps2, coords = c("long","lat"),  crs = 4326)

mrktCAmatched_map2 <- ggplot() +
   geom_sf(data = tregs_shp, aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  # market A locations
   geom_sf(data = mrktAtwards_match_sf, aes(col = region.name.twards), alpha = 0.5, size = 3)+
  # market C locations closest to market A locations
   geom_sf(data = mrktCtoAmatch_sf2, aes(col = region.name.twards.A),  shape = 17, size = 1.5)+
    geom_sf_text(data = tregs_shp, aes(label = Region_Nam), size = 2)+

   scale_colour_manual(values = rep(market_pal,9))+
   coord_sf()+
   labs(title = "Market Survey A (circles) and C (triangles) - C matched to geo-A",
        fill = "Tanzania region",
        col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")
 
mrktCAmatched_map2


ggplot() +
   geom_sf(data = twards_shp %>% filter(Region_Nam %in% c("lindi", "mtwara")), aes(fill = Region_Nam), linewidth = 0.1) +
   scale_fill_manual(values=alpha(tanzania_pal,0.7), guide = "none")+
  # market A locations
   geom_sf(data = mrktAtwards_match_sf%>% filter(region.name.twards %in% c("lindi", "mtwara")), aes(col = region.name.twards), alpha = 0.5, size = 3)+
  # market C locations closest to market A locations
   geom_sf(data = mrktCtoAmatch_sf2%>% filter(region.name.twards.A %in% c("lindi", "mtwara")), aes(col = region.name.twards.A),  shape = 17, size = 1.5)+
   scale_colour_manual(values = rep(market_pal,9))+
   coord_sf(xlim = c(38,39.5), ylim = c(-10,-11.5))+
   labs(title = "Market Survey A (circles) and C (triangles) - C matched to geo-A",
        fill = "Tanzania region",
        col = "Market region")+
  theme(legend.position = "right", legend.box = "horizontal")
```
