---
title: "Tanzania Market Survey C: Data Cleaning"
author: "Beth Savagar"
date: "2023-02-07"
output:
  pdf_document: default
  html_document: default
---

## review Other categories for data to tease out 
# - see excel sheets, recode and reform in mrktdf_definition dataframe

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = F}
library(readr)
library(tidyverse)
library(sf)
library(ggplot2)
library(here)
library(knitr)
library(ggpubr)
library(RColorBrewer)
library(readxl)

```

Produce market C - Activities dataframe for use in MFA


## Load Data:

```{r dataload}

filesave <- F

# mrktc_gps <- read_csv(here("data/tanzania_data/mrktc_allgps_tanzania_final.csv"))
mrktc_gps <- read_csv(here("data/data-cleaning_data/mrktc_allgps_tanzania_final.csv"))

# mrkta_generalinfo, need to link to cleaned update market location data
mrktc_info <-  read_csv(here("data/data-cleaning_data/mrktc_generalinfo_tanzania_final.csv"))

mrktc_activities_raw <- read_csv(here("data/tanzania_data/mrktc_mrktactivities_tanzania.csv"))
```
## Activity lookups:

```{r actvtylkp}

lkp_mrktactvty <- read_csv(here("data/ecopprmarketscsvs/mrktc_lkpmrkt_actvty.csv")) %>%
  mutate(
    Code = as.character(Code),
    `1.mrkt.activity.lkp` = case_match(
      Code,
      "-66" ~ "Other",
      "1" ~ "Selling",
      "2" ~ "Middleman",
      "3" ~ "Trader",
      "4" ~ "Buying"
    )
  )

lkp_sellplacetype <- read_csv(here("data/ecopprmarketscsvs/mrktc_lkpsell_placetype.csv")) %>%
  mutate(
    Code = as.character(Code),
    `2.sell.placetype.lkp` = case_match(
      Code,
      "-66" ~ "Other",
      "1" ~ "Village",
      "2" ~ "Towncentre",
      "3" ~ "Market",
      "4" ~ "Abattoir"
    )
  )

lkp_selltransport <- read_csv(here("data/ecopprmarketscsvs/mrktc_lkpsell_trans.csv")) %>%
  mutate(
    Code = as.character(Code),
    `4.sell.transport.lkp` = case_match(
      Code,
      "-77" ~ "Unknown",
      "-66" ~ "Other",
      "1" ~ "Foot",
      "2" ~ "Vehicle",
      "3" ~ "Cart"
    )
  )

lkp_buyplacetype <- lkp_sellplacetype

lkp_buytransport <- lkp_selltransport

lkp_sellreason <- read_csv(here("data/ecopprmarketscsvs/mrktc_lkpsell_reason.csv"))

lkp_buyreason <- read_csv(here("data/ecopprmarketscsvs/mrktc_lkpbuy_reason.csv"))

```

## Basic data cleaning
- Select and clean variables (columns) of interest:

```{r activitiesClean}

colnames(mrktc_activities_raw)

mrktc_activities_clean1 <- mrktc_activities_raw %>%
  select(
    fid = fid.see.mrktc.generalinfo.,
    # unique.row.id.see.mrktc.generalinfo. # set to 1 for all rows
    # unique.row.id # set to 1 for all rows,
    "1.mrkt.activity" = "1.what.are.the.activities.that.you.are.doing.in.this.market.today.",
    "1.mrkt.activity.other" = "if.other.specify.5",
    "2.sell.placetype.code" = "type.of.place.see.mrktc.lkpsell.placetype.",
    "2.sell.placetype.other" ="if.other.specify",
    "2.sell.place.name" = "name.of.place.8",
    "2.sell.place.ward" = "ward.9",
    "2.sell.place.district" = "district.10",
    "3.sell.reason"="3.what.is.your.main.reason.for.selling.these.sheep.and.or.goats.",
    "3.sell.reason.other"="if.other.specify.12",
    "4.sell.transport.type"="4.how.were.sheep.goats.transported.to.the.market.see.mrktc.lkpsell.trans.",
    "4.sell.transport.other" = "if.other.specify.14",
    # "5.sell.other.species."="5.do.you.also.sell.other.animal.species.apart.from.sheep.and.goats.",
    # "5.sell.species.most"="if.yes.out.of.all.the.species.that.you.sell.which.species.do.you.sell.the.most.",
    # "5.specify.sell.species.most"="if.other.specify.17",
    "6.buy.placetype.code"="type.of.place.see.mrktc.lkpplacetype.",
    "6.buy.placetype.other"="if.other.specify.20",
    "6.buy.place.name" ="name.of.place.21",
    "6.buy.place.ward"="ward.22",
    "6.buy.place.district"="district.23",
    "7.buy.reason"="7.what.is.your.main.reason.for.buying.these.small.ruminants.",
    "7.buy.reason.other" = "if.other.specify.25",
    # "6.buy.transport.yesno" = "will.you.transport.the.sheep.goats.you.are.buying.today.",
    "8.buy.transport.type"="8.how.will.you.transport.these.small.ruminants.that.you.are.buying.see.mrktc.lkpsell.trans.",
    "8.buy.transport.other"="if.other.specify.27",
    # "9.buy.criteria"="9.what.criteria.do.you.use.to.decide.which.small.ruminants.to.buy.",
    # "9.specify.buy.criteria"="if.other.specify.29",
    # "10.buy.species.preference"="10.what.other.species.of.animals.do.you.buy.apart.from.sheep.and.goats.",
    # "10.buy.species.preference.specify"="if.other.specify.31",
    # "11.buy.price.increase" = "11.if.the.prices.of.sheep.and.goats.increase.for.some.reason.e.g.a.shortage.of.animals.due.to.disease.will.you.still.buy.them.",
    # "11.buy.species.alternative" = "if.no.which.other.species.will.you.consider.instead.",
    # "11.buy.species.alternative.specify"="if.other.specify.34",
    # "11.buy.price.increase.details" = "if.yes.how.much.of.an.increase.in.the.current.price.of.sheep.and.goat.unit.price.of.live.animal.will.cause.you.to.change.your.purchasing.behaviour.to.another.animal.species",
    "12.buy.sell.per.month" = "12.how.many.times.in.a.month.do.you.buy.or.sell.sheep.and.or.goats.in.this.market.",
    "unique.row.identifier.uuid."   
  )

colnames(mrktc_activities_clean1)
```


# Clean origin and destination data:

```{r stringclean}

# tolower(``), # lowercase -->
# gsub("[[:punct:]]", " ", ``), # remove punctuation -->
# trimws(``),
# gsub("\\s+", " ", ``))

mrktc_activities_clean2 <- mrktc_activities_clean1 %>% 
  mutate(
    "2.sell.place.name" = tolower(`2.sell.place.name`),
    "2.sell.place.name" = gsub("[[:punct:]]", " ",`2.sell.place.name`),
    "2.sell.place.name" = trimws(`2.sell.place.name`),
    "2.sell.place.name" = gsub("\\s+", ".",`2.sell.place.name`),
    # "2.sell.place.ward",
    "2.sell.place.ward" = tolower(`2.sell.place.ward`),
    "2.sell.place.ward" = gsub("[[:punct:]]", " ",`2.sell.place.ward`),
    "2.sell.place.ward" = trimws(`2.sell.place.ward`),
    "2.sell.place.ward" = gsub("\\s+", ".",`2.sell.place.ward`),
    # "2.sell.place.district"
    "2.sell.place.district" = tolower(`2.sell.place.district`),
    "2.sell.place.district" = gsub("[[:punct:]]", " ",`2.sell.place.district`),
    "2.sell.place.district" = trimws(`2.sell.place.district`),
    "2.sell.place.district" = gsub("\\s+", ".",`2.sell.place.district`),
    
    # "6.buy.place.name"
     "6.buy.place.name" = tolower(`6.buy.place.name`),
    "6.buy.place.name" = gsub("[[:punct:]]", " ",`6.buy.place.name`),
    "6.buy.place.name" = trimws(`6.buy.place.name`),
    "6.buy.place.name" = gsub("\\s+", ".",`6.buy.place.name`),
    # "6.buy.place.ward",
    "6.buy.place.ward" = tolower(`6.buy.place.ward`),
    "6.buy.place.ward" = gsub("[[:punct:]]", " ",`6.buy.place.ward`),
    "6.buy.place.ward" = trimws(`6.buy.place.ward`),
    "6.buy.place.ward" = gsub("\\s+", ".",`6.buy.place.ward`),
    # "6.buy.place.district"
    "6.buy.place.district" = tolower(`6.buy.place.district`),
    "6.buy.place.district" = gsub("[[:punct:]]", " ",`6.buy.place.district`),
    "6.buy.place.district" = trimws(`6.buy.place.district`),
    "6.buy.place.district" = gsub("\\s+", ".",`6.buy.place.district`)
  )

```


#####################
## MARKET ACTIVITY ##
#####################

# 1. Activity at Market:

Multi-choice survey options: 

- Selling
- Middleman
- Trader
- Buying
- Other 
  - slaughter: attending market to slaughter animals (animals from elsewhere or bought at market)
  - food: attending market as food (or meat) vendor. 
  - NB: food vendors may bring/buy live animals, for slaughter then selling as meat/food within the market.

```{r activitiesDetails}
# For fields which contain coded data, use lookups to populate. 

lkp_mrktactvty

# # A tibble: 5 × 4
#   Code  Description                           `Unique Row Identifier (UUID)`       `1.mrkt.activity.lkp`
#   <chr> <chr>                                 <chr>                                <chr>                
# 1 -66   Other (give details)                  72387dd7-bec6-11eb-81ba-3822e2cde809 Other                
# 2 1     Selling my own sheep and/ or goats    7236823f-bec6-11eb-81ba-3822e2cde809 Selling              
# 3 2     Middleman (broker)                    72373132-bec6-11eb-81ba-3822e2cde809 Middleman            
# 4 3     Trader (buying and selling)           7237a10d-bec6-11eb-81ba-3822e2cde809 Trader               
# 5 4     Buying sheep and/ or goats for myself 723813aa-bec6-11eb-81ba-3822e2cde809 Buying  

# Other activities at market:

# write.csv(mrktc_activities_summary %>% distinct(`1.mrkt.activity.other`), file = here("data/data-cleaning_data/mrktactvtyother.csv"))
mrktactvtyother <- read_excel(here("data/data-cleaning_data/mrktactvtyother.xlsx"))

mrktc_activities_v2 <- mrktc_activities_clean2 %>%
  
  # join recoded other activity col:
  left_join(mrktactvtyother %>% 
              select(`1.mrkt.activity.other`, `1.mrkt.activity.other.code`),
            by = c("1.mrkt.activity.other")) %>%
  mutate(`1.mrkt.activity` = gsub(" ", ";", `1.mrkt.activity`)) %>% 
  mutate(
    "1.activity.sell" = if_else(grepl("1", `1.mrkt.activity`), 1, 0),
    "1.activity.sell" = if_else(grepl("sell", `1.mrkt.activity.other.code`), 1, `1.activity.sell`),

    "1.activity.middleman" = if_else(grepl("2", `1.mrkt.activity`), 1, 0),
    "1.activity.middleman" = if_else(grepl("middleman", `1.mrkt.activity.other.code`), 1, `1.activity.middleman`),
    
    "1.activity.trade" = if_else(grepl("3", `1.mrkt.activity`), 1, 0),
    "1.activity.trade" = if_else(grepl("trade", `1.mrkt.activity.other.code`), 1, `1.activity.trade`),
    
    "1.activity.buy" = if_else(grepl("4", `1.mrkt.activity`), 1, 0),
    "1.activity.buy" = if_else(grepl("buy", `1.mrkt.activity.other.code`), 1, `1.activity.buy`),
    
    # additional categories:
    # attending market to slaughter animals (brought from elsewhere or bought at market)
    "1.activity.slaughter" = if_else(grepl("slaughter", `1.mrkt.activity.other.code`), 1, 0),
    
    # attending market to sell meat or food (soup)
    # this may include bringing live animals, which are slaughtered at the market and then meat/food sold.
    "1.activity.food" = if_else(grepl("food", `1.mrkt.activity.other.code`), 1, 0),

    "1.activity.other" = if_else(grepl("other", `1.mrkt.activity.other.code`), 1, 0)
    # "1.activity.other" = if_else(grepl("-66", `1.mrkt.activity`), 1, `1.activity.other`)
    ) %>%
  # calc. if multi activity:
  rowwise() %>%
  mutate(
    "1.activity.multi" = if_else(sum(`1.activity.sell`,`1.activity.buy`,`1.activity.middleman`,`1.activity.trade`,`1.activity.slaughter`, `1.activity.food`, `1.activity.other`)>1,1,0)
  ) %>%
  ungroup()


```

#####################
## SELLING ANIMALS ##
#####################

# 2. Origin Placetype (sellplacetype)

Multi-choice survey options: 

- Village
- Centre/town
- Market
- Abattoir
- Other 


```{r}
lkp_sellplacetype
# 
# # A tibble: 5 × 4
#   Code  Description          `Unique Row Identifier (UUID)`       `2.sell.placetype.lkp`
#   <chr> <chr>                <chr>                                <chr>                 
# 1 -66   Other (give details) 723a71c1-bec6-11eb-81ba-3822e2cde809 Other                 
# 2 1     Village              72390c35-bec6-11eb-81ba-3822e2cde809 Village               
# 3 2     Centre/town          723966cf-bec6-11eb-81ba-3822e2cde809 Towncentre            
# 4 3     Market               7239de7c-bec6-11eb-81ba-3822e2cde809 Market                
# 5 4     Abattoir             723a2cba-bec6-11eb-81ba-3822e2cde809 Abattoir  

# Other sell place
# write.csv(mrktc_activities_summary %>% distinct(`2.sell.placetype.other`), file = here("data/data-cleaning_data/sellplacetypeother.csv"))
sellplaceother <- read_excel(here("data/data-cleaning_data/sellplacetypeother.xlsx"))

mrktc_activities_v3.1 <- mrktc_activities_v2 %>%
  # join recoded other placetype col:
  left_join(sellplaceother %>% 
              select(`2.sell.placetype.other`, `2.sell.placetype.other.code`),
            by = c("2.sell.placetype.other")) %>%
  
  mutate(
    "2.sell.village" = if_else(grepl("1", `2.sell.placetype.code`), 1, 0),
    "2.sell.village" = if_else(grepl("village", `2.sell.placetype.other.code`), 1, `2.sell.village`),
    
    "2.sell.town" = if_else(grepl("2", `2.sell.placetype.code`), 1, 0),
    "2.sell.town" = if_else(grepl("town", `2.sell.placetype.other.code`), 1, `2.sell.town`),
    
    "2.sell.market" = if_else(grepl("3", `2.sell.placetype.code`), 1, 0),
    "2.sell.market" = if_else(grepl("market", `2.sell.placetype.other.code`), 1, `2.sell.market`),
    
    "2.sell.abattoir" = if_else(grepl("4", `2.sell.placetype.code`), 1, 0),
    "2.sell.abattoir" = if_else(grepl("abattoir", `2.sell.placetype.other.code`), 1, `2.sell.abattoir`),
    
    
    "2.sell.otherplace" = if_else(grepl("other", `2.sell.placetype.other.code`), 1, 0))
    # "2.sell.otherplace" = if_else(grepl("-66", `2.sell.placetype.code`), 1, 0),

```

# 3. Sell reason

Multi-choice survey options: 

- Business
- Household needs
- medical
- school
- livestock treatment
- restock
- religious celebration
- other:

New categories:

- *NA_buy*:	NA = not selling animals (buying)
- *householdpersonal* (includes any household, personal needs), as follows:
  - household = general household/personal needs
  - medical = medical needs
  - school = school funds
  - religious = social event
- *slaughter*:	slaughter = animals to slaughter at market
- *food*: food = animals sold as meat/food at market
- *livestock* (includes any livestock related costs):
  - restock = to buy other livestock 
  - livestock = livestock treatment fees
- *agriculture*:	agriculture = animals sold to provide funds for cropping
- *income*:	income = animals sold to earn income
- *informaltrade*:	informaltrade = animals bought and sold at market for informal trade (income, or business)
- *other*:	other = not captured by above categories

```{r}

lkp_sellreason
#   Code Description                          `Unique Row Identifier (UUID)`      
#   <dbl> <chr>                                <chr>                               
# 1   -66 Other selling (give details)         7247685d-bec6-11eb-81ba-3822e2cde809
# 2     1 Business (trader)                    72457d73-bec6-11eb-81ba-3822e2cde809
# 3     2 For household needs - food, clothing 7245ac82-bec6-11eb-81ba-3822e2cde809
# 4     3 Medical bills                        7245e031-bec6-11eb-81ba-3822e2cde809
# 5     4 School fees                          72462b70-bec6-11eb-81ba-3822e2cde809
# 6     5 Livestock treatment costs            7246d36b-bec6-11eb-81ba-3822e2cde809
# 7     6 To buy new animals                   724708ed-bec6-11eb-81ba-3822e2cde809
# 8     7 Religious event                      724737c8-bec6-11eb-81ba-3822e2cde809


# Other sell reason
# write.csv(mrktc_activities_summary %>% distinct(`3.sell.reason.other`), file = here("data/data-cleaning_data/sellreasonother.csv"))
sellotherreason <- read_excel(here("data/data-cleaning_data/sellotherreason.xlsx"), sheet = "sellotherreason")

mrktc_activities_v3.2 <- mrktc_activities_v3.1 %>%    
    # SELL REASON:
    left_join(sellotherreason %>% select(`3.sell.reason.other`, `3.sell.reason.other.code`),
            by = c("3.sell.reason.other")) %>%
    
    # REASONS:
    # 1. Business
      mutate(
    `3.sell.business` = if_else(grepl("1", `3.sell.reason`), 1, 0), 
    `3.sell.business` = if_else(grepl("business", `3.sell.reason.other.code`), 1, `3.sell.business`),
    
     # 2. Household (includes personal, school, medical, religious event)
    `3.sell.household` = if_else(grepl("2|3|4|7", `3.sell.reason`), 1, 0), 
    `3.sell.household` = if_else(grepl("household|medical|school|religious", `3.sell.reason.other.code`), 1, `3.sell.household`),
    
    # 3. Livestock (includes restock, livestockfees)
    `3.sell.livestock` = if_else(grepl("5|6", `3.sell.reason`), 1, 0), 
    `3.sell.livestock` = if_else(grepl("livestock|restock", `3.sell.reason.other.code`), 1, `3.sell.livestock`),
    
    # Other Categories:
    # 4. agriculture = cropping activities
    `3.sell.agriculture` = if_else(grepl("agriculture", `3.sell.reason.other.code`), 1, 0),
    # 5. slaughter = for slaughter at market
    `3.sell.slaughter` = if_else(grepl("slaughter", `3.sell.reason.other.code`), 1, 0),
    # 6. food = for selling meat/food
    `3.sell.food` = if_else(grepl("food", `3.sell.reason.other.code`), 1, 0),
    # 7. informaltrade = buying and selling for income not as business
    `3.sell.informaltrade` = if_else(grepl("informaltrade", `3.sell.reason.other.code`), 1, 0),
    `3.sell.income` = if_else(grepl("income", `3.sell.reason.other.code`), 1, 0),
    # 8. otherreason = not captured above
    `3.sell.otherreason` = if_else(grepl("other", `3.sell.reason.other.code`), 1, 0),
    # 9. NAbuy = buying not selling.
    `3.sell.NAbuy` = if_else(grepl("NA_buy", `3.sell.reason.other.code`), 1, 0)

    ) %>%
  rowwise() %>%
  mutate(`3.sellreason.multi` = if_else(sum(`3.sell.business`,
                                            `3.sell.household`,
                                            `3.sell.livestock`,
                                            `3.sell.agriculture`,
                                            `3.sell.slaughter`,
                                            `3.sell.food`,
                                            `3.sell.informaltrade`,
                                            `3.sell.income`,
                                            `3.sell.otherreason`)>1, 1, 0)) %>% 
  ungroup()

# sellreason should be crossreferenced with activitity at market/ trader ID:
# if ID as trader or middleman/broker then reason = business
# if not ID as trader, then reason = income/informaltrade?


```

# 4. Sell transport

Multi-choice survey options: 

- Foot : by foot
- Vehicle : by car, motorcycle
- Cart : by rickshaw/cart
- Other
- Frommrkt : animal origin is market (no transport)


```{r}
lkp_selltransport

# # A tibble: 5 × 4
#   Code  Description      `Unique Row Identifier (UUID)`       `4.sell.transport.lkp`
#   <chr> <chr>            <chr>                                <chr>                 
# 1 -77   Don't know       723d00f0-bec6-11eb-81ba-3822e2cde809 Unknown               
# 2 -66   Other (describe) 723cbe44-bec6-11eb-81ba-3822e2cde809 Other                 
# 3 1     On foot          723beccf-bec6-11eb-81ba-3822e2cde809 Foot                  
# 4 2     By vehicle       723c33ba-bec6-11eb-81ba-3822e2cde809 Vehicle               
# 5 3     By cart          723c781b-bec6-11eb-81ba-3822e2cde809 Cart   

# Other sell place
# write.csv(mrktc_activities_summary %>% distinct(`4.sell.transport.other`), file = here("data/data-cleaning_data/selltransportother.csv"))

selltransportother <- read_excel(here("data/data-cleaning_data/selltransportother.xlsx"))

mrktc_activities_v4 <- mrktc_activities_v3.2 %>%
  left_join(selltransportother %>% select(`4.sell.transport.other`, `4.sell.transport.other.code`),
            by = c("4.sell.transport.other")) %>%
  mutate(
    "4.sell.foot" = if_else(grepl("1", `4.sell.transport.type`), 1, 0),
    "4.sell.foot" = if_else(grepl("foot", `4.sell.transport.other.code`), 1, `4.sell.foot`),
    
    "4.sell.vehicle" = if_else(grepl("2", `4.sell.transport.type`), 1, 0),
    "4.sell.vehicle" = if_else(grepl("vehicle", `4.sell.transport.other.code`), 1, `4.sell.vehicle`),
    
    "4.sell.cart" = if_else(grepl("3", `4.sell.transport.type`), 1, 0),
    "4.sell.cart" = if_else(grepl("cart", `4.sell.transport.other.code`), 1, `4.sell.cart`),
    
    "4.sell.frommrkt" = if_else(grepl("market", `4.sell.transport.other.code`), 1, 0),
    
    "4.sell.othertransport" = if_else(grepl("-66", `4.sell.transport.type`), 1, 0),
    "4.sell.othertransport" = if_else(grepl("other", `4.sell.transport.other.code`), 1, `4.sell.othertransport`),
    
    "4.sell.unknowntransport" = if_else(grepl("-77", `4.sell.transport.type`), 1, 0),
    "4.sell.unknowntransport" = if_else(grepl("unknown", `4.sell.transport.other.code`), 1, `4.sell.unknowntransport`),
  )

```


#####################
## BUYING ANIMALS ##
#####################

# 5. Destination Placetype (buyplacetype)

Multi-choice survey options: 

- Village
- Centre/town
- Market
- Abattoir
- Other 

```{r}


# # A tibble: 5 × 4
#   Code  Description          `Unique Row Identifier (UUID)`       `2.sell.placetype.lkp`
#   <chr> <chr>                <chr>                                <chr>                 
# 1 -66   Other (give details) 723a71c1-bec6-11eb-81ba-3822e2cde809 Other                 
# 2 1     Village              72390c35-bec6-11eb-81ba-3822e2cde809 Village               
# 3 2     Centre/town          723966cf-bec6-11eb-81ba-3822e2cde809 Towncentre            
# 4 3     Market               7239de7c-bec6-11eb-81ba-3822e2cde809 Market                
# 5 4     Abattoir             723a2cba-bec6-11eb-81ba-3822e2cde809 Abattoir  


# Other buy place
# write.csv(mrktc_activities_summary %>% distinct(`6.buy.placetype.other`), file = here("data/data-cleaning_data/buyplacetypeother.csv"))
buyplaceother <- read_excel(here("data/data-cleaning_data/buyplacetypeother.xlsx"))


mrktc_activities_v5.1 <- mrktc_activities_v4 %>%
  left_join(buyplaceother %>% select(`6.buy.placetype.other`, `6.buy.placetype.other.code`),
            by = c("6.buy.placetype.other")) %>%
  mutate(
    "6.buy.village" = if_else(grepl("1", `6.buy.placetype.code`), 1, 0),
    "6.buy.village" = if_else(grepl("village", `6.buy.placetype.other.code`), 1, `6.buy.village`),
    
    "6.buy.town" = if_else(grepl("2", `6.buy.placetype.code`), 1, 0),
    "6.buy.town" = if_else(grepl("town", `6.buy.placetype.other.code`), 1, `6.buy.town`),
    
    "6.buy.market" = if_else(grepl("3", `6.buy.placetype.code`), 1, 0),
    "6.buy.market" = if_else(grepl("market", `6.buy.placetype.other.code`), 1, `6.buy.market`),
    
    "6.buy.abattoir" = if_else(grepl("4", `6.buy.placetype.code`), 1, 0),
    "6.buy.abattoir" = if_else(grepl("slaughter", `6.buy.placetype.other.code`), 1, `6.buy.abattoir`),
    
    "6.buy.otherplace" = if_else(grepl("other", `6.buy.placetype.other.code`), 1, 0))
```


# 6. Buy reason

Multi-choice survey options: 

- Business
- restock
- breeding
- fattening
- rearing
- home consumption
- religious/social event
- abattoir/slaughter
- other: 

New categories:

- *NA_sell*:	NA = not buying animals (selling)
- *food*: food = bought for food / meat business (may include slaughter)
- *income*:	income = animals bought to earn income (buying & reselling)
- *informaltrade*:	informaltrade = animals bought and sold at market for informal trade (income, or business)
- *other*:	other = not captured by above categories

```{r}

lkp_buyreason
# # A tibble: 9 × 3
#    Code Description                            `Unique Row Identifier (UUID)`      
#   <dbl> <chr>                                  <chr>                               
# 1   -66 Other buying (give details)            72453231-bec6-11eb-81ba-3822e2cde809
# 2     1 Business (trader)                      72429617-bec6-11eb-81ba-3822e2cde809
# 3     2 Re-stocking                            72432f4c-bec6-11eb-81ba-3822e2cde809
# 4     3 Breeding stock                         72436bc2-bec6-11eb-81ba-3822e2cde809
# 5     4 Fattening                              7243cb4d-bec6-11eb-81ba-3822e2cde809
# 6     5 Rearing                                72442a15-bec6-11eb-81ba-3822e2cde809
# 7     6 For home consumption                   7244779c-bec6-11eb-81ba-3822e2cde809
# 8     7 Religious or social event              7244bc8d-bec6-11eb-81ba-3822e2cde809
# 9     8 To take to the abattoir/slaughter slab 7244f996-bec6-11eb-81ba-3822e2cde809

# Other buy reason
# write.csv(mrktc_activities_summary %>% distinct(`7.buy.reason.other`), file = here("data/data-cleaning_data/buyreasonother.csv"))

buyreasonother <- read_excel(here("data/data-cleaning_data/buyreasonother.xlsx"))

  
  # BUY REASON
mrktc_activities_v5.2 <- mrktc_activities_v5.1 %>%
  
  left_join(buyreasonother %>% select(`7.buy.reason.other`, `7.buy.reason.other.code`),
            by = c("7.buy.reason.other")) %>%

     ### reason
  mutate(
    `7.buy.business` = if_else(grepl("1", `7.buy.reason`), 1, 0), 
    `7.buy.business` = if_else(grepl("business", `7.buy.reason.other.code`), 1, `7.buy.business`),
    
    `7.buy.restock` = if_else(grepl("2", `7.buy.reason`), 1, 0), 
    `7.buy.restock` = if_else(grepl("restock", `7.buy.reason.other.code`), 1, `7.buy.restock`),
    
    `7.buy.breedstock` = if_else(grepl("3", `7.buy.reason`), 1, 0), 
    `7.buy.breedstock` = if_else(grepl("breedstock", `7.buy.reason.other.code`), 1, `7.buy.breedstock`),
    
    `7.buy.fattening` = if_else(grepl("4", `7.buy.reason`), 1, 0), 
    `7.buy.fattening` = if_else(grepl("fattening", `7.buy.reason.other.code`), 1, `7.buy.fattening`),
    
    `7.buy.rearing` = if_else(grepl("5", `7.buy.reason`), 1, 0), 
    `7.buy.rearing` = if_else(grepl("rearing", `7.buy.reason.other.code`), 1, `7.buy.rearing`),
    
    `7.buy.homereligious` = if_else(grepl("6|7", `7.buy.reason`), 1, 0), 
    `7.buy.homereligious` = if_else(grepl("home|religious", `7.buy.reason.other.code`), 1, `7.buy.homereligious`),
    
    `7.buy.slaughter` = if_else(grepl("8", `7.buy.reason`), 1, 0),
    `7.buy.slaughter` = if_else(grepl("slaughter", `7.buy.reason.other.code`), 1, `7.buy.slaughter`),
    
    # other categories:
    `7.buy.food` = if_else(grepl("food", `7.buy.reason.other.code`), 1, 0),
    `7.buy.informaltrade` = if_else(grepl("informaltrade", `7.buy.reason.other.code`), 1,0),
    `7.buy.income` = if_else(grepl("income", `7.buy.reason.other.code`), 1, 0),
    
    `7.buy.otherreason` =  if_else(grepl("other", `7.buy.reason.other.code`), 1, 0),
    `7.buy.NAsell` = if_else(grepl("sell", `7.buy.reason.other.code`), 1, 0)
    ) %>%
  rowwise() %>%
    mutate(`7.buyreason.multi` = if_else(sum(`7.buy.business`,
                                            `7.buy.restock`,
                                            `7.buy.breedstock`,
                                            `7.buy.fattening`,
                                            `7.buy.rearing`,
                                            `7.buy.homereligious`,
                                            `7.buy.slaughter`,
                                            `7.buy.food`,
                                            `7.buy.informaltrade`,
                                            `7.buy.income`,
                                            `7.buy.otherreason`
                                            )>1, 1, 0)
    ) %>% 
  ungroup()

# Other buy reason
# 
# write.csv(mrktc_activities_summary %>% distinct(`7.buy.reason.other`), file = here("data/data-cleaning_data/buyreasonother.csv"))

```

7. Buy transport

```{r}
lkp_buytransport

# # A tibble: 5 × 4
#   Code  Description      `Unique Row Identifier (UUID)`       `4.sell.transport.lkp`
#   <chr> <chr>            <chr>                                <chr>                 
# 1 -77   Don't know       723d00f0-bec6-11eb-81ba-3822e2cde809 Unknown               
# 2 -66   Other (describe) 723cbe44-bec6-11eb-81ba-3822e2cde809 Other                 
# 3 1     On foot          723beccf-bec6-11eb-81ba-3822e2cde809 Foot                  
# 4 2     By vehicle       723c33ba-bec6-11eb-81ba-3822e2cde809 Vehicle               
# 5 3     By cart          723c781b-bec6-11eb-81ba-3822e2cde809 Cart   

# write.csv(mrktc_activities_summary %>% distinct(`8.buy.transport.other`), file = here("data/data-cleaning_data/buytransportother.csv"))

buytransportother <- read_excel(here("data/data-cleaning_data/buytransportother.xlsx"))

mrktc_activities_v6 <- mrktc_activities_v5.2 %>%
  left_join(buytransportother %>% select(`8.buy.transport.other`,`8.buy.transport.other.code`),
            by = c("8.buy.transport.other")) %>%
  mutate(
    "8.buy.foot" = if_else(grepl("1", `8.buy.transport.type`), 1, 0),
    "8.buy.foot" = if_else(grepl("foot", `8.buy.transport.other.code`), 1, `8.buy.foot`),
    
    "8.buy.vehicle" = if_else(grepl("2", `8.buy.transport.type`), 1, 0),
    "8.buy.vehicle" = if_else(grepl("vehicle", `8.buy.transport.other.code`), 1, `8.buy.vehicle`),
    
    "8.buy.cart" = if_else(grepl("3", `8.buy.transport.type`), 1, 0),
    "8.buy.cart" = if_else(grepl("cart", `8.buy.transport.other.code`), 1, `8.buy.cart`),
    
    "8.buy.slaughter" = if_else(grepl("slaughter", `8.buy.transport.other.code`), 1, 0),
    "8.buy.atmarket" = if_else(grepl("atmrkt", `8.buy.transport.other.code`), 1, 0),
    
    "8.buy.othertransport" = if_else(grepl("other", `8.buy.transport.other.code`), 1, 0),
    "8.buy.unknowntransport" = if_else(grepl("-77", `8.buy.transport.type`), 1, 0)
  )


```

#####################
## BUYSELL per MONTH ##
#####################

```{r}

mrktc_activities_v6 %>% select(`12.buy.sell.per.month`) %>% summary()
mrktc_activities_v6 %>% distinct(`12.buy.sell.per.month`) # remove any > 24

mrktc_activities_v7 <- mrktc_activities_v6 %>%
  mutate(`12.buy.sell.per.month` = if_else(`12.buy.sell.per.month`>30, NA, `12.buy.sell.per.month`))

```

```{r }

mrktc_activities_v7 %>% colnames()

mrktc_activities_summary <- mrktc_activities_v7 %>%
  select(
    fid, 
    starts_with("1."),
    starts_with("2.sell.place."),
    starts_with("2.sell.placetype."),
    starts_with("2.sell."),
    starts_with("3."),
    starts_with("4."),
    starts_with("6.buy.place."),
    starts_with("6.buy.placetype."),
    starts_with("6.buy."),
    starts_with("7."),
    starts_with("8."),
    starts_with("12."),
    unique.row.identifier.uuid.
  )



```



```{r saveActvty}
if(filesave){
  write_csv(mrktc_activities_summary, file = here("data/data-cleaning_data/mrktc_mrktactivities_tanzania_final.csv"))
  write_csv(mrktc_activities_summary, file = here("data/tanzania_data/mrktc_mrktactivities_tanzania_final.csv"))
}

```


## ORIGIN WARDS:


```{r originwards}
# tolower(``), # lowercase -->
# gsub("[[:punct:]]", " ", ``), # remove punctuation -->
# trimws(``),
# gsub("\\s+", " ", ``))

mrktc_activities_v6 %>% distinct(`2.sell.place.ward`, `2.sell.place.district`)

mrktc_activities_v6 %>% distinct(`2.sell.place.ward`)

mrktc_activities_v6 %>% distinct(`2.sell.place.district`) %>% arrange()

```

